---
title: "02-SnailLevel"
author: "Galina M. Jönsson"
date: "16/10/2020"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

# 1. Introduction

<br/>
<br/>

## Tidy and standardise raw data

Load and tidy the data. These analyses are based on the data sets, each of which contains data on different levels: snail-level, survey-level and Shehia-level. We therefore start by reading each in turn, assigning all variables within a data set the correct class.

```{r load-data, cache=TRUE, warning=FALSE, message=FALSE}
#############################################################################
####### Snail-level data set - test result for infection per snail ##########
#############################################################################
# Load data set
snailRaw <- read.csv("../Data/rawData/snail_xeno_raw.csv")
## Assign variables appropriate classes
snailRaw$`snail_id`<-as.factor(snailRaw$`snail_id`)
snailRaw$`site`<-as.factor(snailRaw$`site`)
snailRaw$`survey`<-as.factor(snailRaw$`survey`)
snailRaw$`shehia`<-as.factor(snailRaw$`shehia`)
snailRaw$`type`<-as.factor(snailRaw$`type`)
snailRaw$`zest_arm`<-as.factor(snailRaw$`zest_arm`)
snailRaw$`survey_site`<-as.factor(snailRaw$`survey_site`)
snailRaw$`survey_shehia`<-as.factor(snailRaw$`survey_shehia`)
snailRaw$`wbtype`<-as.factor(snailRaw$`wbtype`)
snailRaw$`wbtype2`<-as.integer(snailRaw$`wbtype2`)
snailRaw$`assumed_Bulinus_spp_site`<-as.factor(snailRaw$`assumed_Bulinus_spp_site`)
snailRaw$`ITS-1-2-F_outcome`<-as.factor(snailRaw$`ITS_1_2_F_outcome`)
snailRaw$prepat_schisto_sp<-as.factor(snailRaw$prepat_schisto_sp)
snailRaw$prepat_Sh<-as.factor(snailRaw$prepat_Sh)
snailRaw$prepat_Sb<-as.factor(snailRaw$prepat_Sb)
snailRaw$prepat_ShSb<-as.factor(snailRaw$prepat_ShSb)
snailRaw$prepat_Schisto<-as.factor(snailRaw$prepat_Schisto)
snailRaw$Sh_all<-as.character(snailRaw$Sh_all)
snailRaw$Sh_all<-as.integer(snailRaw$Sh_all)
snailRaw$Sb_all<-as.character(snailRaw$Sb_all)
snailRaw$Sb_all<-as.integer(snailRaw$Sb_all)
snailRaw$'ITSF_2_outcome'<-as.factor(snailRaw$'ITSF_2_outcome')
snailRaw$'conf_Bulinus_sp'<-as.factor(snailRaw$'conf_Bulinus_sp')
snailRaw$'Bulinus_haplo'<-as.factor(snailRaw$'Bulinus_haplo')
snailRaw$patent_Sh<-as.factor(snailRaw$patent_Sh)
snailRaw$patent_Sb<-as.factor(snailRaw$patent_Sb)
snailRaw$patent_Schisto<-as.factor(snailRaw$patent_Schisto)


#############################################################################
#### Survey-level data set - environmental variables + human activities #####
#############################################################################
## Load data set
surveyRaw <- read.csv("../Data/rawData/survey_site_raw.csv")
## Assign variables appropriate classes
surveyRaw$`site`<-as.factor(surveyRaw$`USI`)
surveyRaw$`survey`<-as.factor(surveyRaw$`survey`)
surveyRaw$`shehia`<-as.factor(surveyRaw$`shehia`)
surveyRaw$`type`<-as.factor(surveyRaw$`type`)
surveyRaw$`zest_arm`<-as.factor(surveyRaw$`zest_arm`)
surveyRaw$`survey_site`<-as.factor(surveyRaw$`survey_site`)
surveyRaw$`survey_shehia`<-as.factor(surveyRaw$`survey_shehia`)
surveyRaw$`wbtype`<-as.factor(surveyRaw$`wbtype`)
surveyRaw$`wbtype2`<-as.integer(surveyRaw$`wbtype2`)
surveyRaw$`wlevel`<-as.factor(surveyRaw$`wlevel`)
surveyRaw$`BgBn_pres`<-as.factor(surveyRaw$`BgBn_pres`)
surveyRaw$`cerc_sp`<-as.factor(surveyRaw$`cerc_sp`)
surveyRaw$`flow`<-as.factor(surveyRaw$`flow`)
surveyRaw$`depth`<-as.factor(surveyRaw$`depth`)
surveyRaw$`Bfor_pres`<-as.factor(surveyRaw$`Bfor_pres`)
surveyRaw$`Lym_pres`<-as.factor(surveyRaw$`Lym_pres`)
surveyRaw$`Mel_pres`<-as.factor(surveyRaw$`Mel_pres`)
surveyRaw$`Cleo_pres`<-as.factor(surveyRaw$`Cleo_pres`)
surveyRaw$`Pila_pres`<-as.factor(surveyRaw$`Pila_pres`)
surveyRaw$`Lan_pres`<-as.factor(surveyRaw$`Lan_pres`)
surveyRaw$`Thiara_pres`<-as.factor(surveyRaw$`Thiara_pres`)
surveyRaw$`other_snail`<-as.factor(surveyRaw$`other_snail`)
surveyRaw$`Lilies`<-as.factor(surveyRaw$`Lilies`)
surveyRaw$`rushes`<-as.factor(surveyRaw$`rushes`)
surveyRaw$`rice`<-as.factor(surveyRaw$`rice`)
surveyRaw$waterhyacinth<-as.factor(surveyRaw$waterhyacinth)
surveyRaw$palmfronds<-as.factor(surveyRaw$palmfronds)
surveyRaw$sedge<-as.factor(surveyRaw$sedge)
surveyRaw$grass<-as.factor(surveyRaw$grass)
surveyRaw$banana<-as.factor(surveyRaw$banana)
surveyRaw$veg_any<-as.factor(surveyRaw$veg_any)
surveyRaw$mud<-as.factor(surveyRaw$mud)
surveyRaw$sand<-as.factor(surveyRaw$sand)
surveyRaw$rock<-as.factor(surveyRaw$rock)
surveyRaw$concrete<-as.factor(surveyRaw$concrete)
surveyRaw$roots<-as.factor(surveyRaw$roots)
surveyRaw$Litter<-as.factor(surveyRaw$Litter)
surveyRaw$`Dead.wood`<-as.factor(surveyRaw$`Dead.wood`)
surveyRaw$wudu<-as.factor(surveyRaw$wudu)
surveyRaw$bathing<-as.factor(surveyRaw$bathing)
surveyRaw$clothes<-as.factor(surveyRaw$clothes)
surveyRaw$dishes<-as.factor(surveyRaw$dishes)
surveyRaw$carbike<-as.factor(surveyRaw$carbike)
surveyRaw$collectingwater<-as.factor(surveyRaw$collectingwater)
surveyRaw$swimmingplaying<-as.factor(surveyRaw$swimmingplaying)
surveyRaw$fishing<-as.factor(surveyRaw$fishing)
surveyRaw$Ricecult<-as.factor(surveyRaw$Ricecult)
surveyRaw$otherfarming<-as.factor(surveyRaw$otherfarming)
surveyRaw$sanitation<-as.factor(surveyRaw$sanitation)
surveyRaw$water_contact<-as.factor(surveyRaw$water_contact)
surveyRaw$cow<-as.factor(surveyRaw$cow)
surveyRaw$goat<-as.factor(surveyRaw$goat)
surveyRaw$donkey<-as.factor(surveyRaw$donkey)
surveyRaw$ungulate<-as.factor(surveyRaw$ungulate)


#############################################################################
###### Shehia-level data set - infection rates among school children ########
#############################################################################
### Load data set
shehiaRaw <- read.csv("../Data/rawData/shehia_school_raw.csv")
## Assign variables appropriate classes
shehiaRaw$`shehia`<-as.factor(shehiaRaw$`shehia`)
shehiaRaw$`type`<-as.factor(shehiaRaw$`type`)
shehiaRaw$`zest_arm`<-as.factor(shehiaRaw$`zest_arm`)
```
<br/>

Now we merge the data sets to get one data set where each individual *Bulinus* individual (snailRaw) also has information on environmental variables from where it was collected (surveyRaw) and infection rates among school children in the Shehia from where it was collected (shehiaRaw). Finally, we tidy the resulting data set. 
```{r MergeTidy-data, cache=TRUE, warning=FALSE, message=FALSE}
### Merge snailRaw and surveyRaw based on "survey_site" and keep all observations in snailRaw
snailDFtemp1 <- merge(snailRaw, surveyRaw, by.x="survey_site", by.y="survey_site", all.x=TRUE)
# Double check we haven't lost/duplicated any observations
#nrow(snailRaw) == nrow(snailDFtemp1) 

### Merge snailDFtemp1 and shehiaRaw based on shehia and keep all observations in snailRaw/snailDFtemp1
snailDFtemp2 <-merge(snailDFtemp1, shehiaRaw, by.x="shehia.x", by.y="shehia", all.x=TRUE)
# Double check we haven't lost/duplicated any observations
#nrow(snailRaw) == nrow(snailDFtemp2) 

### Subset columns of interest and create a new data frame with only these columns
snailDF <- snailDFtemp2[c("shehia.x", "survey_site", "snail_id", 
                        "site.x", "survey.x", "type.x",
                        "survey_shehia.x", "wbtype.x", 
                        "wbtype2.x", "lat_Cor", "lon_Cor",
                        "Sh_all", "wlevel", "BgBn_number", "temp", 
                        "ph", "cond", "tds", "sal", "flow", 
                        "depth", "Bfor_pres", "other_snail", 
                        "swimmingplaying", "bathing", 
                        "clothes", "dishes", "collectingwater",
                        "Ricecult", "otherfarming")]

### Rename certain variables for convenience
require(dplyr)
snailDF <- snailDF %>% 
  rename(
    shehia = shehia.x, 
    site = site.x, 
    survey = survey.x, 
    type = type.x, 
    survey_shehia = survey_shehia.x, 
    wbtype = wbtype.x,
    wbtype2 = wbtype2.x
    )
# As we will use "site" nested in "shehia" as random variables, we will remove any sites with six or fewer snails. See the number of snails in each site commented next to the site name below
temp <- nrow(snailDF)
snailDF <- filter(snailDF, site != "Mat7") # 3
snailDF <- filter(snailDF, site != "Mat12") # 3
snailDF <- filter(snailDF, site != "Wam7") # 3
snailDF <- filter(snailDF, site != "Ole13") # 6
snailDF <- filter(snailDF, site != "Waw5") # 5
snailDF <- filter(snailDF, site != "Uku10") # 6
# How many observations were removed?
#temp - nrow(snailDF) # 26

### Create ordered variables for ordered factor variables
snailDF$type <- factor(snailDF$type, ordered = TRUE, 
                                levels = c("HNR", "HD", "LNR", "LD"))
snailDF$wbtype <- factor(snailDF$wbtype, ordered = TRUE, 
                                levels = c("1", "2", "3", "4", "5", "6", "7"))
snailDF$wlevel <- factor(snailDF$wlevel, ordered = TRUE, 
                                levels = c("1", "2", "3", "4"))
snailDF$flow <- factor(snailDF$flow, ordered = TRUE, 
                                levels = c("1", "2", "3", "4"))
snailDF$depth <- factor(snailDF$depth, ordered = TRUE, 
                                levels = c("1", "2", "3"))

### Change binary variables to integers
snailDF$Bfor_pres <- as.integer(as.character(snailDF$Bfor_pres))
snailDF$other_snail <- as.integer(as.character(snailDF$other_snail))
snailDF$swimmingplaying <- as.integer(as.character(snailDF$swimmingplaying))
snailDF$bathing <- as.integer(as.character(snailDF$bathing))
snailDF$clothes <- as.integer(as.character(snailDF$clothes))
snailDF$dishes <- as.integer(as.character(snailDF$dishes))
snailDF$collectingwater <- as.integer(as.character(snailDF$collectingwater))
snailDF$Ricecult <- as.integer(as.character(snailDF$Ricecult))
snailDF$otherfarming <- as.integer(as.character(snailDF$otherfarming))

### Create a data frame where all observations have data for all above variables
snailDF.na <- na.omit(snailDF)
# How many observations were removed?
#nrow(snailDF) - nrow(snailDF.na) # 1335
# Drop unused levels from both tidied data sets
snailDF <- droplevels(snailDF)
snailDF.na <- droplevels(snailDF.na)
```
<br/>
<br/>

## Variables

<br/>

Here, we inspect our response variable and explanatory variables of potential interetst to inform our model formulation.  

<br/>
<br/>

### Response variable
The response variable used in these analyses is "Sh_all", which denotes whether each snail was infected (1) or (0). 


<br/>
<br/>
```{r respvar, cache=TRUE, message=FALSE, echo=FALSE}
require(ggplot2)
require(dplyr)

### How many are infected (1) and not (0)? 
# Plot distribution of response variable
snailDF.na %>% 
  mutate(y = Sh_all %>% as.factor()) %>% 
  ggplot(aes(x = Sh_all)) +
  geom_bar(stat = "count") +
  stat_count(geom = "text", colour = "white", size = 3.5,
             aes(label = ..count..),position=position_stack(vjust=0.5)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 4000)) +
  theme(panel.grid = element_blank()) +
  labs(x = "Infection Status",
       y = "Individual Count",
       title ="Figure 1.1: Infection status among analysed Bolinus sp. individuals",
       subtitle = "Where 1 and 0 denote infected an uninfected, respectively") +
  theme(panel.background = element_rect(fill = "white", colour = "black")) +
  theme(text = element_text(size = 12))  
```
<br/>

96%, i.e. the majority, of tested individuals were not infected (3963), whilst 4% were (153). 

<br/>
<br/>

### Potential explanatory variables

<br/>

##### Explanatory variables of potential interest

* **wlevel** -> water level (ordered categorical expressed as numeric 1:4, where 1 denotes flooded, 2 = normal, 3 = low, 4= dry)    
* **wbtype2** -> waterbody type: either permanent (1) or temporary (0)    
* **syrvey** -> four surveys; corresponds to time of year; potentially correlated with wlevel and wbtype2    
* **temp** -> water temperature (*C)   
* **cond** -> conductivity; indirect measure of water chemistry   
* **ph** -> potentially correlated with conductivity   
* **type** -> human response to treatment per shehia; whether people got reinfected quickly or not; four categories    
* **tds** -> total dissolved substances; likely correlated with cond and/or sal    
* **sal** -> water salinity; likely correlated with tds, pH and/or sal   
* **flow** -> water flow in four categories   
* **depth** -> water depth in three categories; likely correlated with wbtype2   
* **Swimmingplaying** -> water contract will increase likelihood of snail infection - also this is children swimming and playing and these are the higher risk group for infections based on the disease endemicity (INFORMATIVE PRIOR)   
* **bathing** -> water contract will increase likelihood of snail infection, however people may also be less likely to urinate in these areas because people bathing in them? I would suggest we go with INFORMATIVE that it will increase snail infection now though since there is water contact happening and this is key   
* **othersnail** -> uninformative - presence of other snails may cause 'miracidial sponges' (when schistosomes infect the wrong snail species), however just theory based so we shouldn't use as a prior, but the outcome of model will be interesting.   

<br/>
**IF POSSIBLE** <span style="color: red;">**Note: these variables will not be included in model fitting**</span> 

* **Bfor_pres** -> This will be duplicated in the 'othersnail' column since that is a summary stat of any other snail species present, but this species presence may be of particular interest out of the other snail species... This is another closely related Bulinus species Bulinus forskalii that does not transmit schistosomes on Pemba (although does in West Africa) - however its presence in Pemba might confuse the schistosomes if release similar attractants to the other Bulinus species making the miracidia attempt to infect them. This a very loose theory but could be interesting! :)    
* **clothes** -> uninformative    
* **dishes** -> uninformative    
* **collectingwater** -> uninformative   
* **ricecult** -> uninformative   
* **otherfarming** -> uninformative   

<br/>
<br/>

### Test for collinearity between explanatory variables

<br/>

Potential collinearity between quantitative explanatory variables is tested using the Kendall rank coefficient to establish whether variables are statistically dependent. This test is non-parametric, i.e. does not rely on any assumptions on the distributions of the variables so there is no need for transformations of the data. We display the results in below correlation chart (Figure 2; significance levels are associated to a symbol such that p-values of 0.001, 0.01 and 0.05 are indicated by three, two and one asterisks, respectively).  

<br/>
```{r collinearity-explanVars-test1, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
require("PerformanceAnalytics"); require("ggplot2"); require("ggpubr")
### Quantitative explanatory variables: Kendall rank coefficient
chart.Correlation(snailDF.na[,c("temp", "ph", "cond", "tds", "sal")], 
                  histogram=TRUE, pch=19, method = "kendall")
mtext("Figure 1.2: Correlation chart of contious variables (Kendall rank coefficient)", side=3, line=3) # add legend
```
<br/>
<br/>
The majority of explanatory quantitative variables are correlated (p<0.001), and therefore not independent. As such, by the end of the model selection process we want a model that **ONLY includes one quantitative variable**, because including two or more independent variables does not meet model assumptions. All correlation coefficients except between pH and total dissolved substances are significantly correlated, and therefore, the only scenario in which we would include two explanatory quantitative variables is those two. Moreover, all correlation coefficients between conductivity, total dissolved substances and salinity are very close to 1 and have p<0.001. Therefore, we will **disregard total dissolved substances and salinity** from hereon and only consider conductivity in model formulations because, among the three, this variable was measured most precisely. 
<br/>


<br/>
Potential collinearity between qualitative and quantitative explanatory variables is visually examined using box plots:
<br/>

<br/>
```{r collinearity-explanVars-test2, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
require("PerformanceAnalytics"); require("ggplot2"); require("ggpubr")
## Qualitative variables and temp
figure1.3 <- ggarrange(ggplot(snailDF.na, aes(x = type, y = temp)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = wbtype2, y = temp)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = survey, y = temp)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = wlevel, y = temp)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = flow, y = temp)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = depth, y = temp)) + geom_boxplot() + theme_bw() +
                         rremove("x.text"), 
                       #labels = c("type", "wbtype2", "survey", "wlevel", "flow", "depth"),
                       ncol = 3, nrow = 2)
annotate_figure(figure1.3,
               top = text_grob("Figure 1.3: Box plots - Temperature against qualitative variables", 
                               size = 14))
```
<br/>
<br/>
Figure 1.3 (above) indicates that we do not have collinearity between temperature and any of the qualitative variables as evident from overlapping interquartile ranges (boxes) for all variables except survey-value 'S3' and remaining survey-values (top right panel), but note that the whiskers still overlap. Also note that, unsurprisingly, the most evident case of potential collinearity between temperature and a qualitative variables is for depth (bottom right panel); however, the differences are not statistically significant as evident from overlaps. As such, we do not need to worry about potentially combining temperature and any of the qualitative variables in model formulations. 
<br/>

<br/>
```{r collinearity-explanVars-test3, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
require("PerformanceAnalytics"); require("ggplot2"); require("ggpubr")
## Qualitative variables and ph
figure1.4 <- ggarrange(ggplot(snailDF.na, aes(x = type, y = ph)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = wbtype2, y = ph)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = survey, y = ph)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = wlevel, y = ph)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = flow, y = ph)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = depth, y = ph)) + geom_boxplot() + theme_bw() +
                         rremove("x.text"), ncol = 3, nrow = 2)
annotate_figure(figure1.4,
               top = text_grob("Figure 1.4: Box plots - pH against qualitative variables", 
                               size = 14))
```
<br/>
<br/>
Figure 1.4 (above) indicates that we do not have collinearity between pH and any of the qualitative variables as evident from overlapping interquartile ranges (boxes). As with temperature (Figure 1.3) , the most evident case of potential collinearity is for depth (bottom right panel); however, the differences are not statistically significant. As such, we do not need to worry about potentially combining pH and any of the qualitative variables in model formulations. 
<br/>

<br/>
```{r collinearity-explanVars-test4, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
require("PerformanceAnalytics"); require("ggplot2"); require("ggpubr")
## Qualitative variables and cond
figure1.5 <- ggarrange(ggplot(snailDF.na, aes(x = type, y = cond)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = wbtype2, y = cond)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = survey, y = cond)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = wlevel, y = cond)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = flow, y = cond)) + geom_boxplot() + theme_bw(),
                       ggplot(snailDF.na, aes(x = depth, y = cond)) + geom_boxplot() + theme_bw() +
                         rremove("x.text"), ncol = 3, nrow = 2)
annotate_figure(figure1.5,
               top = text_grob("Figure 1.5: Box plots - Conductivity against qualitative variables", 
                               size = 14))
```
<br/>
<br/>
Figure 1.5 (above) indicates that we also do not have collinearity between conductivity and the qualitative variables so we do not need to worry about potentially combining conductivity and any of the qualitative variables in model formulations. 
<br/>
<br/>
<br/>



# 2. Model fitting and selection


### Prior specifications
We apply prior distributions to all explanatory variables of potential interest that reflect our actual beliefs and understandings. Our explanatory variables and prior specifications are as follows:

* **wlevel** -> water level    
* **wbtype2** -> waterbody type: either permanent or temporary    
* **syrvey** -> four surveys; corresponds to time of year; potentially correlated with wlevel and wbtype2; this variable will not be dropped in any model simplification as it accounts for known differences in between different seasons.  
* **temp** -> water temperature in degrees Celsius per survey within the range 22.33C to 33.81C. Although multiple authors have shown that the interplay between the snail:parasite is limited by temperature (mechanism not confirmed), we know/do not know whether it is within the temperature ranges tested here. As such we chose a prior distribution that reflects our this knowledge/lack thereof: a normal prior with mean 0/1/2/3/4 and standard deviation 10. **UPDATE MARCH 2022**: we will use an uninformative prior because its hypothesis-based and existing research is on another species: a normal prior with mean 0 and standard deviation 10. 
* **cond** -> conductivity, which is an indirect measure of water chemistry   
* **ph** ->  
* **type** -> human response to treatment (i.e. the degree to which infected individuals became reinfected) per shehia, which is divided into four categories. We expect responses to treatment to be an indirect measure of human behavior , such that individuals inhabiting shesias with low rates of reinfection are more likely to exhibit less "risky" behaviors compared to those inhabiting Shesias with high rates of reinfection. **UPDATE MARCH 2022**: we will use an uninformative prior because its hypothesis-driven: a normal prior with mean 0 and standard deviation 10. Hence, we use a       

(set_prior("normal(0,10)", class = "b"

"Families binomial, bernoulli, Beta, zero_inflated_binomial, zero_inflated_beta, and zero_one_inflated_beta support logit, probit, probit_approx, cloglog, cauchit, and identity."


##### Useful links
* https://mran.microsoft.com/snapshot/2016-02-05/web/packages/brms/vignettes/brms.pdf   
* https://bookdown.org/ajkurz/DBDA_recoded/jags-brms.html    
* https://www.rensvandeschoot.com/tutorials/brms-started/   
* https://www.rensvandeschoot.com/tutorials/brms-priors/   
* https://www.rensvandeschoot.com/brms-wambs/   
* https://mran.microsoft.com/snapshot/2016-02-05/web/packages/brms/vignettes/brms.pdf (Added **December 2020**)   
* https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/1365-2656.13087 (Added **December 2020**)   
* https://cran.r-project.org/web/packages/brms/brms.pdf (Added **December 2020**)   
* https://bayesat.github.io/lund2018/slides/andrey_anikin_slides.pdf (Added **December 2020**)   
* https://www.rensvandeschoot.com/tutorials/generalised-linear-models-with-brms/ (Added **December 2020**)   

## Maximal-minimal 1st iteration

### Fit maximal model
```{r Sh_all-drop1-max-fit-20220430, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
### Generate maximal model output using new cloglog-formulation
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
max1st_V2 <-brm(data = snailDF.na, 
             family = bernoulli(link = cloglog), 
             formula = Sh_all ~ # Response variable
               wbtype2 + wlevel + type + survey + flow + depth + temp + cond + ph + 
               swimmingplaying + bathing + other_snail + # Fixed effects
               (1|survey) + (1|shehia/site), # Random effects w/ interaction
             warmup = 5000, # burn-in period (i.e. iterations to be discarded)
             iter = 15000, # total number of iterations (inc. burn-in)
             chains = 3, # number of MCMC chains
             inits  = 0,  # starting values of the iterations
             seed = 666, # random seed, allowing for replication of results
             thin = 3, # thinning for manageable model output file size
             cores = 2, #  to speed up modelling time
             control = list(adapt_delta = 0.999)) 
### Check for convergence and divergent transitions before saving output
max1st_V2 
#saveRDS(max1st_V2, "../Data/ModelOutputs/InfectionPrevalence/max1st_V2.rds")
```




### Bayesian Binary logistic Regression (with Non-Informative Priors)

First, we run a model with uninformative priors fitted to all parameters. Each random effect of each grouping factor has a standard deviation parameter, which is restricted to be non-negative and, by default, has a half Cauchy prior with a scale parameter that scales with the standard deviation of the response variable. 

```{r Sh_all-UNINF-fit, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE, echo=FALSE}
require("brms")

### Fit a maximal model with uninformative priors 
#max.noInfo <-
#  brm(data = snailDF.na, 
#      family = bernoulli(link = logit), # specify bernoulli (not binomial) for a binary logistic regression
#      formula = Sh_all ~ # Response variable
#        wbtype2 + wlevel + type + survey + flow + depth +
#            temp + cond + ph + 
#              swimmingplaying + bathing + other_snail +
#              Bfor_pres + clothes + dishes + collectingwater +
#              Ricecult + otherfarming +
#            (1|shehia/site), # Random factor
#      warmup = 5000, # burn-in period (i.e. iterations to be discarded)
#      iter = 15000, # total number of iterations (including burn-in)
#      chains = 3, # number of MCMC 
#      inits  = 0, # inits specifies the starting values of the iterations (normally you can either use the maximum likelihood estimates of the parameters as starting values, or simply ask the algorithm to start with zeros)
#      seed = 666) # specifies the random seed, allowing for replication of results

# Save object
#saveRDS(max.noInfo, "../Data/ModelOutputs/InfectionPrevalence/max.noInfo.rds")
```







```{r Sh_all-UNINF-eval, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
require("brms")

# Read the maximal model file with no informative priors
max.noInfo <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max.noInfo.rds")

# Quick look at the summary
summary(max.noInfo)

# Plot the effect
plot(max.noInfo)
```

Interestingly, the model does not seem to struggle to converge despite the large number of explanatory variables  as evident from Rhat values of 1 and "furry caterpillars" but 95% credible intervals overlap zero for nearly all variables, indicating that we could certainly get rid of some variables. We do this using leave-one-out cross-validation (LOOCV) but first we must refit the maximal model dropping each explanatory variable in turn. The five variables that do not, or only marginally, overlap zero (wlevel, depth, temperature, ph and Bfor_pres) will not be dropped initially.  




```{r Sh_all-UNINF-drop1, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE, echo=FALSE}
require("brms")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop wbtype2
max1_wbtype2_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wlevel + type + survey + flow + depth + temp + cond + ph + 
                        swimmingplaying + bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_wbtype2_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_wbtype2_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop wlevel
max1_wlevel_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + type + survey + flow + depth + temp + cond + ph + 
                        swimmingplaying + bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_wlevel_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_wlevel_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop type
max1_type_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + flow + depth + temp + cond + ph + 
                        swimmingplaying + bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_type_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_type_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop flow
max1_flow_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + type + depth + temp + cond + ph + 
                        swimmingplaying + bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_flow_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_flow_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop depth
max1_depth_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + type + flow + temp + cond + ph + 
                        swimmingplaying + bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_depth_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_depth_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop temp
max1_temp_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + type + flow + depth + cond + ph + 
                        swimmingplaying + bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_temp_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_temp_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop cond
max1_cond_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + type + flow + depth + temp + ph + 
                        swimmingplaying + bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_cond_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_cond_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop ph
max1_ph_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + type + flow + depth + temp + cond + 
                        swimmingplaying + bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_ph_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_ph_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop swimmingplaying
max1_swimmingplaying_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + type + flow + depth + temp + cond + ph +
                        bathing + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_swimmingplaying_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_swimmingplaying_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop bathing
max1_bathing_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + type + flow + depth + temp + cond + ph +
                        swimmingplaying + other_snail + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_bathing_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_bathing_V2.rds")
#############################################################################
###########################   NOT GENERATED   ###############################
#############################################################################
### Drop other_snail
max1_other_snail_V2 <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                      formula = Sh_all ~ wbtype2 + wlevel + survey + type + flow + depth + temp + cond + ph +
                        swimmingplaying + bathing + (1|survey) + (1|shehia/site), 
                      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666, 
                      thin = 3, cores = 2, control = list(adapt_delta = 0.999)) 
saveRDS(max1_other_snail_V2, "../Data/ModelOutputs/InfectionPrevalence/max1_other_snail_V2.rds")


#############################################################################
############################   GOT TO HERE   ################################
#############################################################################
```

\n
\n




### GOT TO HERE 30 April 2022






## Maximal-minimal 1st iteration

### Fit maximal model
```{r Sh_all-drop1-max-fit, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")

### Maximal
max1st <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit), # specify bernoulli (not binomial) for a binary logistic regression
      formula = Sh_all ~ # Response variable
        wbtype2 + wlevel + type + survey + flow + depth + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), # Random factor
      warmup = 5000, # burn-in period (i.e. iterations to be discarded)
      iter = 15000, # total number of iterations (including burn-in)
      chains = 3, # number of MCMC 
      inits  = 0, # inits specifies the starting values of the iterations (normally you can either use the maximum likelihood estimates of the parameters as starting values, or simply ask the algorithm to start with zeros)
      seed = 666) # specifies the random seed, allowing for replication of results

# Save object
#saveRDS(max1st, "../Data/ModelOutputs/InfectionPrevalence/max1st.rds")
```

### Inspect maximal model
```{r Sh_all-drop1-max, message=FALSE, warning=FALSE, cache=TRUE, eval=TRUE}
require("brms")
# Read model output
max1st <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st.rds")

# Quick look at the summary
summary(max1st)

# Plot the effect
plot(max1st)
```
Interestingly, the model does not seem to struggle to converge despite the large number of explanatory variables  as evident from Rhat values of 1 and "furry caterpillars" but 95% credible intervals overlap zero for nearly all variables, indicating that we could certainly get rid of some variables. We do this using lPareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO-CV) but first we must refit the maximal model dropping each explanatory variable in turn. The five variables that do not, or only marginally, overlap zero (wlevel, depth, temperature, ph and Bfor_pres) will not be dropped initially.  

### Fit leave-one-out models
```{r Sh_all-drop1, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")

### Drop wbtype2
max1st_drop_wbtype2 <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wlevel + type + survey + flow + depth + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_wbtype2, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_wbtype2.rds")

### Drop wlevel
max1st_drop_wlevel <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + type + survey + flow + depth + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_wlevel, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_wlevel.rds")

### Drop type
max1st_drop_type <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + flow + depth + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_type, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_type.rds")

### Drop flow
max1st_drop_flow <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + depth + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_flow, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_flow.rds")

### Drop depth
max1st_drop_depth <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + flow + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_depth, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_depth.rds")

### Drop temp
max1st_drop_temp <- 
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + flow + depth + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_temp, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_temp.rds")

### Drop cond
max1st_drop_cond <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + flow + depth + temp + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_cond, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_cond.rds")

### Drop ph
max1st_drop_ph <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + flow + depth + temp + cond + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_ph, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_ph.rds")

### Drop swimmingplaying
max1st_drop_swimmingplaying <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + flow + depth + temp + cond + ph + 
        bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_swimmingplaying, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_swimmingplaying.rds")

### Drop bathing
max1st_drop_bathing <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + flow + depth + temp + cond + ph + 
        swimmingplaying + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_bathing, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_bathing.rds")

### Drop other_snail
max1st_drop_other_snail <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + flow + depth + temp + cond + ph + 
        swimmingplaying + bathing +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max1st_drop_other_snail, "../Data/ModelOutputs/InfectionPrevalence/max1st_drop_other_snail.rds")
```




### Model Comparison: Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) 


We use the loo package to carry out Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) for purposes of model checking and model comparison.   
- Reference: https://link.springer.com/article/10.1007/s11222-016-9696-4  
- Useful link: https://mc-stan.org/loo/articles/loo2-example.html   
We compare three models at a time for html markdown to knit because the process is computationally expensive and the Pareto smoothed importance-sampling objects are approx 1GB per model.




```{r PSISLOO-1st, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
library("loo")
# Read objects
max1st_drop_wbtype2 <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_wbtype2.rds")
max1st_drop_wlevel <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_wlevel.rds")
max1st_drop_type <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_type.rds")
max1st_drop_flow <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_flow.rds")
max1st_drop_depth <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_depth.rds")
max1st_drop_temp <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_temp.rds")
max1st_drop_cond <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_cond.rds")
max1st_drop_ph <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_ph.rds")
max1st_drop_swimmingplaying <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_swimmingplaying.rds")
max1st_drop_bathing <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_bathing.rds")
max1st_drop_other_snail <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_other_snail.rds")

# compute PSIS-LOO values with the loo function
#loo_max.noInfo.flow <- loo(max.noInfo.flow, save_psis = TRUE)
loo_max1st_drop_wbtype2 <- loo(max1st_drop_wbtype2, save_psis = TRUE)
loo_max1st_drop_wlevel <- loo(max1st_drop_wlevel, save_psis = TRUE)
loo_max1st_drop_type <- loo(max1st_drop_type, save_psis = TRUE)
loo_max1st_drop_flow <- loo(max1st_drop_flow, save_psis = TRUE)
loo_max1st_drop_depth <- loo(max1st_drop_depth, save_psis = TRUE)
loo_max1st_drop_temp <- loo(max1st_drop_temp, save_psis = TRUE)
loo_max1st_drop_cond <- loo(max1st_drop_cond, save_psis = TRUE)
loo_max1st_drop_ph <- loo(max1st_drop_ph, save_psis = TRUE)
loo_max1st_drop_swimmingplaying <- loo(max1st_drop_swimmingplaying, save_psis = TRUE)
loo_max1st_drop_bathing <- loo(max1st_drop_bathing, save_psis = TRUE)
loo_max1st_drop_other_snail <- loo(max1st_drop_other_snail, save_psis = TRUE)
# Compare PSIS-LOO values
loo_compare(loo_max1st_drop_wbtype2, loo_max1st_drop_wlevel, 
            loo_max1st_drop_type, loo_max1st_drop_flow,
            loo_max1st_drop_depth,  loo_max1st_drop_temp,
            loo_max1st_drop_cond, loo_max1st_drop_ph,
            loo_max1st_drop_swimmingplaying, loo_max1st_drop_bathing,
            loo_max1st_drop_other_snail)
```
                            elpd_diff se_diff
max1st_drop_flow             0.0       0.0   
max1st_drop_other_snail     -2.4       1.2   
max1st_drop_cond            -2.7       1.3   
max1st_drop_bathing         -3.1       0.7   
max1st_drop_type            -3.2       1.1   
max1st_drop_wbtype2         -3.5       1.2   
max1st_drop_ph              -3.6       1.8   
max1st_drop_swimmingplaying -3.9       0.9   
max1st_drop_temp            -5.0       3.3   
max1st_drop_wlevel          -8.6       5.4   
max1st_drop_depth           -9.7       5.3  

## Maximal-minimal 2nd iteration

### Inspect maximal model
Lets have a look before dropping further variables
```{r Sh_all-drop2-max, message=FALSE, warning=FALSE, cache=TRUE}
require("brms")

max1st_drop_flow <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_flow.rds")

# Quick look at the summary
summary(max1st_drop_flow)

# Plot the effect
plot(max1st_drop_flow)
```


### Fit leave-one-out models
We're dropping flow first and re-running dropping eahc variable in turn
```{r Sh_all-drop2, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")

### Drop wbtype2
max2nd_drop_wbtype2 <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wlevel + type + survey + depth + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_wbtype2, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_wbtype2.rds")

### Drop wlevel
max2nd_drop_wlevel <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + type + survey + depth + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_wlevel, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_wlevel.rds")

### Drop type
max2nd_drop_type <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + depth + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_type, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_type.rds")

### Drop depth
max2nd_drop_depth <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + temp + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_depth, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_depth.rds")

### Drop temp
max2nd_drop_temp <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + depth + cond + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_temp, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_temp.rds")

### Drop cond
max2nd_drop_cond <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + depth + temp + ph + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_cond, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_cond.rds")

### Drop ph
max2nd_drop_ph <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + depth + temp + cond + 
        swimmingplaying + bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_ph, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_ph.rds")

### Drop swimmingplaying
max2nd_drop_swimmingplaying <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + depth + temp + cond + ph + 
        bathing + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_swimmingplaying, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_swimmingplaying.rds")

### Drop bathing
max2nd_drop_bathing <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + depth + temp + cond + ph + 
        swimmingplaying + other_snail +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_bathing, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_bathing.rds")

### Drop other_snail
max2nd_drop_other_snail <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + type + survey + depth + temp + cond + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max2nd_drop_other_snail, "../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_other_snail.rds")
```

### Model Comparison: Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) 
```{r PSISLOO-2nd, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
library("loo")
# Read objects
max1st_drop_flow <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max1st_drop_flow.rds")
max2nd_drop_wbtype2 <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_wbtype2.rds")
max2nd_drop_wlevel <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_wlevel.rds")
max2nd_drop_type <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_type.rds")
max2nd_drop_depth <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_depth.rds")
max2nd_drop_temp <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_temp.rds")
max2nd_drop_cond <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_cond.rds")
max2nd_drop_ph <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_ph.rds")
max2nd_drop_swimmingplaying <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_swimmingplaying.rds")
max2nd_drop_bathing <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_bathing.rds")
max2nd_drop_other_snail <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_other_snail.rds")
# compute PSIS-LOO values with the loo function
loo_max1st_drop_flow <- loo(max1st_drop_flow, save_psis = TRUE)
loo_max2nd_drop_wbtype2 <- loo(max2nd_drop_wbtype2, save_psis = TRUE)
loo_max2nd_drop_wlevel <- loo(max2nd_drop_wlevel, save_psis = TRUE)
loo_max2nd_drop_type <- loo(max2nd_drop_type, save_psis = TRUE)
loo_max2nd_drop_depth <- loo(max2nd_drop_depth, save_psis = TRUE)
loo_max2nd_drop_temp <- loo(max2nd_drop_temp, save_psis = TRUE)
loo_max2nd_drop_cond <- loo(max2nd_drop_cond, save_psis = TRUE)
loo_max2nd_drop_ph <- loo(max2nd_drop_ph, save_psis = TRUE)
loo_max2nd_drop_swimmingplaying <- loo(max2nd_drop_swimmingplaying, save_psis = TRUE)
loo_max2nd_drop_bathing <- loo(max2nd_drop_bathing, save_psis = TRUE)
loo_max2nd_drop_other_snail <- loo(max2nd_drop_other_snail, save_psis = TRUE)
# Compare PSIS-LOO values
loo_compare(loo_max1st_drop_flow, loo_max2nd_drop_wbtype2, 
            loo_max2nd_drop_wlevel, loo_max2nd_drop_type, 
            loo_max2nd_drop_depth,  loo_max2nd_drop_temp,
            loo_max2nd_drop_cond, loo_max2nd_drop_ph,
            loo_max2nd_drop_swimmingplaying, loo_max2nd_drop_bathing,
            loo_max2nd_drop_other_snail)
```
                            elpd_diff se_diff
max2nd_drop_other_snail      0.0       0.0   
max2nd_drop_bathing         -0.5       0.7   
max2nd_drop_type            -0.6       0.9   
max2nd_drop_cond            -1.0       1.5   
max2nd_drop_wbtype2         -1.2       0.9   
max2nd_drop_swimmingplaying -1.2       0.8   
max1st_drop_flow            -1.2       0.9   
max2nd_drop_ph              -1.4       1.9   
max2nd_drop_temp            -5.2       3.6   
max2nd_drop_wlevel          -8.1       5.7   
max2nd_drop_depth           -9.7       5.2  




## Maximal-minimal 3rd iteration

### Inspect maximal model
Lets have a look before dropping further variables
```{r Sh_all-drop3-max, message=FALSE, warning=FALSE, cache=TRUE}
require("brms")

max2nd_drop_other_snail <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_other_snail.rds")

# Quick look at the summary
summary(max2nd_drop_other_snail)

# Plot the effect
plot(max2nd_drop_other_snail)
```





### Fit leave-one-out models
We're dropping flow first and re-running dropping eahc variable in turn
```{r Sh_all-drop3, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")

### Drop wbtype2
max3rd_drop_wbtype2 <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wlevel + type + survey + depth + temp + cond + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_wbtype2, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_wbtype2.rds")

### Drop wlevel
max3rd_drop_wlevel <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + type + survey + depth + temp + cond + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_wlevel, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_wlevel.rds")

### Drop type
max3rd_drop_type <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + depth + temp + cond + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_type, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_type.rds")

### Drop depth
max3rd_drop_depth <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + temp + cond + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_depth, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_depth.rds")

### Drop temp
max3rd_drop_temp <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + cond + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_temp, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_temp.rds")

### Drop cond
max3rd_drop_cond <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_cond, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_cond.rds")

### Drop ph
max3rd_drop_ph <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + cond + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_ph, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_ph.rds")

### Drop swimmingplaying
max3rd_drop_swimmingplaying <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + cond + ph +
        bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_swimmingplaying, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_swimmingplaying.rds")

### Drop bathing
max3rd_drop_bathing <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + cond + ph +
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max3rd_drop_bathing, "../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_bathing.rds")
```


### Model Comparison: Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) 
```{r PSISLOO-3rd, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
library("loo")
# Read objects
max2nd_drop_other_snail <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max2nd_drop_other_snail.rds")
max3rd_drop_wbtype2 <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_wbtype2.rds")
max3rd_drop_wlevel <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_wlevel.rds")
max3rd_drop_type <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_type.rds")
max3rd_drop_depth <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_depth.rds")
max3rd_drop_temp <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_temp.rds")
max3rd_drop_cond <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_cond.rds")
max3rd_drop_ph <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_ph.rds")
max3rd_drop_swimmingplaying <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_swimmingplaying.rds")
max3rd_drop_bathing <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_bathing.rds")
# compute PSIS-LOO values with the loo function
loo_max2nd_drop_other_snail <- loo(max2nd_drop_other_snail, save_psis = TRUE)
loo_max3rd_drop_wbtype2 <- loo(max3rd_drop_wbtype2, save_psis = TRUE)
loo_max3rd_drop_wlevel <- loo(max3rd_drop_wlevel, save_psis = TRUE)
loo_max3rd_drop_type <- loo(max3rd_drop_type, save_psis = TRUE)
loo_max3rd_drop_depth <- loo(max3rd_drop_depth, save_psis = TRUE)
loo_max3rd_drop_temp <- loo(max3rd_drop_temp, save_psis = TRUE)
loo_max3rd_drop_cond <- loo(max3rd_drop_cond, save_psis = TRUE)
loo_max3rd_drop_ph <- loo(max3rd_drop_ph, save_psis = TRUE)
loo_max3rd_drop_swimmingplaying <- loo(max3rd_drop_swimmingplaying, save_psis = TRUE)
loo_max3rd_drop_bathing <- loo(max3rd_drop_bathing, save_psis = TRUE)
# Compare PSIS-LOO values
loo_compare(loo_max2nd_drop_other_snail, loo_max3rd_drop_wbtype2, 
            loo_max3rd_drop_wlevel, loo_max3rd_drop_type, 
            loo_max3rd_drop_depth,  loo_max3rd_drop_temp,
            loo_max3rd_drop_cond, loo_max3rd_drop_ph,
            loo_max3rd_drop_swimmingplaying, loo_max3rd_drop_bathing)
```
                            elpd_diff se_diff
max3rd_drop_cond              0.0       0.0  
max3rd_drop_bathing          -0.4       0.9  
max3rd_drop_type             -0.6       1.0  
max2nd_drop_other_snail      -1.2       0.9  
max3rd_drop_wbtype2          -1.3       1.2  
max3rd_drop_swimmingplaying  -1.4       1.0  
max3rd_drop_ph               -1.5       1.9  
max3rd_drop_temp             -5.4       4.1  
max3rd_drop_wlevel           -8.3       5.8  
max3rd_drop_depth           -10.3       5.2 

We're dropping cond


## Maximal-minimal 4th iteration

### Inspect maximal model
Lets have a look before dropping further variables
```{r Sh_all-drop4-max, message=FALSE, warning=FALSE, cache=TRUE}
require("brms")

max3rd_drop_cond <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_cond.rds")

# Quick look at the summary
summary(max3rd_drop_cond)

# Plot the effect
plot(max3rd_drop_cond)
```



### Fit leave-one-out models
```{r Sh_all-drop4, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")

### Drop wbtype2
max4th_drop_wbtype2 <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wlevel + survey + type + depth + temp + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max4th_drop_wbtype2, "../Data/ModelOutputs/InfectionPrevalence/max4th_drop_wbtype2.rds")

### Drop wlevel
max4th_drop_wlevel <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + type + survey + depth + temp + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max4th_drop_wlevel, "../Data/ModelOutputs/InfectionPrevalence/max4th_drop_wlevel.rds")

### Drop type
max4th_drop_type <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + depth + temp + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max4th_drop_type, "../Data/ModelOutputs/InfectionPrevalence/max4th_drop_type.rds")

### Drop depth
max4th_drop_depth <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + temp + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max4th_drop_depth, "../Data/ModelOutputs/InfectionPrevalence/max4th_drop_depth.rds")

### Drop temp
max4th_drop_temp <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + ph + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max4th_drop_temp, "../Data/ModelOutputs/InfectionPrevalence/max4th_drop_temp.rds")

### Drop ph
max4th_drop_ph <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + 
        swimmingplaying + bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max4th_drop_ph, "../Data/ModelOutputs/InfectionPrevalence/max4th_drop_ph.rds")

### Drop swimmingplaying
max4th_drop_swimmingplaying <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + ph +
        bathing + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max4th_drop_swimmingplaying, "../Data/ModelOutputs/InfectionPrevalence/max4th_drop_swimmingplaying.rds")

### Drop bathing
max4th_drop_bathing <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + ph +
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max4th_drop_bathing, "../Data/ModelOutputs/InfectionPrevalence/max4th_drop_bathing.rds")
```



### Model Comparison: Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) 
```{r PSISLOO-4th, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
library("loo")
# Read objects
max3rd_drop_cond <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max3rd_drop_cond.rds")
max4th_drop_wbtype2 <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_wbtype2.rds")
max4th_drop_wlevel <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_wlevel.rds")
max4th_drop_type <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_type.rds")
max4th_drop_depth <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_depth.rds")
max4th_drop_temp <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_temp.rds")
max4th_drop_ph <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_ph.rds")
max4th_drop_swimmingplaying <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_swimmingplaying.rds")
max4th_drop_bathing <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_bathing.rds")
# compute PSIS-LOO values with the loo function
loo_max3rd_drop_cond <- loo(max3rd_drop_cond, save_psis = TRUE)
loo_max4th_drop_wbtype2 <- loo(max4th_drop_wbtype2, save_psis = TRUE)
loo_max4th_drop_wlevel <- loo(max4th_drop_wlevel, save_psis = TRUE)
loo_max4th_drop_type <- loo(max4th_drop_type, save_psis = TRUE)
loo_max4th_drop_depth <- loo(max4th_drop_depth, save_psis = TRUE)
loo_max4th_drop_temp <- loo(max4th_drop_temp, save_psis = TRUE)
loo_max4th_drop_ph <- loo(max4th_drop_ph, save_psis = TRUE)
loo_max4th_drop_swimmingplaying <- loo(max4th_drop_swimmingplaying, save_psis = TRUE)
loo_max4th_drop_bathing <- loo(max4th_drop_bathing, save_psis = TRUE)
# Compare PSIS-LOO values
loo_compare(loo_max3rd_drop_cond, loo_max4th_drop_wbtype2, 
            loo_max4th_drop_wlevel, loo_max4th_drop_type, 
            loo_max4th_drop_depth,  loo_max4th_drop_temp,
            loo_max4th_drop_ph, loo_max4th_drop_swimmingplaying, 
            loo_max4th_drop_bathing)
```
                            elpd_diff se_diff
max4th_drop_bathing          0.0       0.0   
max4th_drop_type            -0.2       0.7   
max3rd_drop_cond            -0.5       0.7   
max4th_drop_wbtype2         -0.6       1.0   
max4th_drop_swimmingplaying -1.1       1.1   
max4th_drop_ph              -1.4       2.1   
max4th_drop_temp            -6.6       3.9   
max4th_drop_wlevel          -7.8       5.5   
max4th_drop_depth           -9.7       5.2  

We're dropping bathing

## Maximal-minimal 5th iteration

### Inspect maximal model
Lets have a look before dropping further variables

```{r Sh_all-drop5-max, message=FALSE, warning=FALSE, cache=TRUE}
require("brms")

max4th_drop_bathing <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_bathing.rds")

# Quick look at the summary
summary(max4th_drop_bathing)

# Plot the effect
plot(max4th_drop_bathing)
```


### Fit leave-one-out models
```{r Sh_all-drop5, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")

### Drop wbtype2
max5th_drop_wbtype2 <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wlevel + survey + type + depth + temp + ph + 
        swimmingplaying +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max5th_drop_wbtype2, "../Data/ModelOutputs/InfectionPrevalence/max5th_drop_wbtype2.rds")

### Drop wlevel
max5th_drop_wlevel <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + type + survey + depth + temp + ph + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max5th_drop_wlevel, "../Data/ModelOutputs/InfectionPrevalence/max5th_drop_wlevel.rds")

### Drop type
max5th_drop_type <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + depth + temp + ph + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max5th_drop_type, "../Data/ModelOutputs/InfectionPrevalence/max5th_drop_type.rds")

### Drop depth
max5th_drop_depth <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + temp + ph + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max5th_drop_depth, "../Data/ModelOutputs/InfectionPrevalence/max5th_drop_depth.rds")

### Drop temp
max5th_drop_temp <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + ph + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max5th_drop_temp, "../Data/ModelOutputs/InfectionPrevalence/max5th_drop_temp.rds")

### Drop ph
max5th_drop_ph <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max5th_drop_ph, "../Data/ModelOutputs/InfectionPrevalence/max5th_drop_ph.rds")

### Drop swimmingplaying
max5th_drop_swimmingplaying <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + type + depth + temp + ph +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max5th_drop_swimmingplaying, "../Data/ModelOutputs/InfectionPrevalence/max5th_drop_swimmingplaying.rds")
```


### Model Comparison: Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) 
```{r PSISLOO-5th, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
library("loo")
# Read objects
max4th_drop_bathing <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max4th_drop_bathing.rds")
max5th_drop_wbtype2 <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_wbtype2.rds")
max5th_drop_wlevel <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_wlevel.rds")
max5th_drop_type <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_type.rds")
max5th_drop_depth <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_depth.rds")
max5th_drop_temp <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_temp.rds")
max5th_drop_ph <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_ph.rds")
max5th_drop_swimmingplaying <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_swimmingplaying.rds")
# compute PSIS-LOO values with the loo function
loo_max4th_drop_bathing <- loo(max4th_drop_bathing, save_psis = TRUE)
loo_max5th_drop_wbtype2 <- loo(max5th_drop_wbtype2, save_psis = TRUE)
loo_max5th_drop_wlevel <- loo(max5th_drop_wlevel, save_psis = TRUE)
loo_max5th_drop_type <- loo(max5th_drop_type, save_psis = TRUE)
loo_max5th_drop_depth <- loo(max5th_drop_depth, save_psis = TRUE)
loo_max5th_drop_temp <- loo(max5th_drop_temp, save_psis = TRUE)
loo_max5th_drop_ph <- loo(max5th_drop_ph, save_psis = TRUE)
loo_max5th_drop_swimmingplaying <- loo(max5th_drop_swimmingplaying, save_psis = TRUE)

# Compare PSIS-LOO values
loo_compare(loo_max4th_drop_bathing, loo_max5th_drop_wbtype2, 
            loo_max5th_drop_wlevel, loo_max5th_drop_type, 
            loo_max5th_drop_depth,  loo_max5th_drop_temp,
            loo_max5th_drop_ph, loo_max5th_drop_swimmingplaying)
```
                            elpd_diff se_diff
max5th_drop_type             0.0       0.0   
max4th_drop_bathing         -0.4       0.8   
max5th_drop_swimmingplaying -0.4       0.8   
max5th_drop_wbtype2         -0.5       1.0   
max5th_drop_ph              -1.3       1.9   
max5th_drop_temp            -6.5       3.7   
max5th_drop_wlevel          -8.2       5.3   
max5th_drop_depth           -9.5       5.0 


## Maximal-minimal 6th iteration

### Inspect maximal model
Lets have a look before dropping further variables

```{r Sh_all-drop6-max, message=FALSE, warning=FALSE, cache=TRUE}
require("brms")
require("PerformanceAnalytics")
require("ggplot2")
require("ggpubr")

max5th_drop_type <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_type.rds")

# Quick look at the summary
summary(max5th_drop_type)

# Plot the effect
plot(max5th_drop_type)
```




### Fit leave-one-out models
```{r Sh_all-drop6, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")

### Drop wbtype2
max6th_drop_wbtype2 <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wlevel + survey + depth + temp + ph + 
        swimmingplaying +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max6th_drop_wbtype2, "../Data/ModelOutputs/InfectionPrevalence/max6th_drop_wbtype2.rds")

### Drop wlevel
max6th_drop_wlevel <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + survey + depth + temp + ph + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max6th_drop_wlevel, "../Data/ModelOutputs/InfectionPrevalence/max6th_drop_wlevel.rds")

### Drop depth
max6th_drop_depth <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + temp + ph + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max6th_drop_depth, "../Data/ModelOutputs/InfectionPrevalence/max6th_drop_depth.rds")

### Drop temp
max6th_drop_temp <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + depth + ph + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max6th_drop_temp, "../Data/ModelOutputs/InfectionPrevalence/max6th_drop_temp.rds")

### Drop ph
max6th_drop_ph <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + depth + temp + 
        swimmingplaying + 
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max6th_drop_ph, "../Data/ModelOutputs/InfectionPrevalence/max6th_drop_ph.rds")

### Drop swimmingplaying
max6th_drop_swimmingplaying <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ 
        wbtype2 + wlevel + survey + depth + temp + ph +
        (1|shehia/site), 
      warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666) 
# Save object
saveRDS(max6th_drop_swimmingplaying, "../Data/ModelOutputs/InfectionPrevalence/max6th_drop_swimmingplaying.rds")
```


### Model Comparison: Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) 
```{r PSISLOO-6th, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
library("loo")
# Read objects
max5th_drop_type <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max5th_drop_type.rds")
max6th_drop_wbtype2 <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max6th_drop_wbtype2.rds")
max6th_drop_wlevel <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max6th_drop_wlevel.rds")
max6th_drop_depth <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max6th_drop_depth.rds")
max6th_drop_temp <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max6th_drop_temp.rds")
max6th_drop_ph <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max6th_drop_ph.rds")
max6th_drop_swimmingplaying <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max6th_drop_swimmingplaying.rds")
# compute PSIS-LOO values with the loo function
loo_max5th_drop_type <- loo(max5th_drop_type, save_psis = TRUE)
loo_max6th_drop_wbtype2 <- loo(max6th_drop_wbtype2, save_psis = TRUE)
loo_max6th_drop_wlevel <- loo(max6th_drop_wlevel, save_psis = TRUE)
loo_max6th_drop_depth <- loo(max6th_drop_depth, save_psis = TRUE)
loo_max6th_drop_temp <- loo(max6th_drop_temp, save_psis = TRUE)
loo_max6th_drop_ph <- loo(max6th_drop_ph, save_psis = TRUE)
loo_max6th_drop_swimmingplaying <- loo(max6th_drop_swimmingplaying, save_psis = TRUE)
# Compare PSIS-LOO values
loo_compare(loo_max5th_drop_type, loo_max6th_drop_wbtype2, 
            loo_max6th_drop_wlevel, loo_max6th_drop_depth,  
            loo_max6th_drop_temp, loo_max6th_drop_ph, 
            loo_max6th_drop_swimmingplaying)
```
                            elpd_diff se_diff
max5th_drop_type             0.0       0.0   
max6th_drop_swimmingplaying  0.0       0.5   
max6th_drop_wbtype2         -0.2       0.4   
max6th_drop_ph              -0.8       1.6   
max6th_drop_temp            -5.8       3.7   
max6th_drop_wlevel          -7.6       5.4   
max6th_drop_depth           -9.2       5.2  






# 3. Model fitting and selection - 29/4/2022  Update
<br/>
<br/>

#### Notes TP-GMJ meeting 29/4/2022 

* Decision taken to NOT drop wbtype2 (so we delete the 8th and 9th iterations) because its potential effect is a hypothesis TP wants to test.  
* Decision taken to make 'survey' a random variable. The reasoning behind having it as a fixed effect is that the four surveys were taken during the four seasons of one year. However, there is no replicate year (i.e. all surveys were taken during one year so we can't infer anything about the effect of season per se) and although we do expect the level of infection among snails to differ between seasons, we do not belive that it is the season in itself that is the effect but other variables which we already have (e.g. temperature).  
* Finally, we know that ph and temperature are highly correlated so we will drop the one that has least explanatory power.  

<br/>
<br/>

## Model implementation & selection

Given the inherently "low information content" of binary data, we will fit our binomial generalised linear mixed effects model using **Bayesian inference**. We will use the R package **brms**, which implements Bayesian generalized linear mixed models using the probabilistic programming language **Stan**. Please see the [brms github page](https://github.com/paul-buerkner/brms) for software installation guides (available for multiple operation systems). Moreover, "brms" allows model fit to be assessed and compared with the **Watanabe-Akaike-Information Criterion (WAIC)** and **leave-one-out cross-validation (LOOCV)**. We Will use WAIC LOO for model selection. 

<br/>
<br/>

### Model Specifications 

* The response variable and explanatory variables are described and visualised under section '1. Introduction'. In addition to these variables, we want to account for the following **three random factors**:  
    + **Shehia**: regions/wards on Pemba.  <br/>
    + **Site**: site ID within Shesias. Hence, we must specify that **site is nested within Shehia**; i.e., the effect of site is dependent on the Shehia because, in this case, they are physically nested and we cannot have one site in more than one Shehia.  <br/>
    + **Survey**: all sites were surveyed four times over the curse of one year; although surveys correlate with season of one year, there is no replicate year (i.e. all surveys were taken during one year so we can't infer anything about the effect of season *per se*). Moreover, despite expecting the level of infection among snails vary between seasons, we do not believe that it is the season in itself that is the cause other factors included in the model (e.g. temperature).  <br/>
* **Distribution Family**: Since our data is binary (a snail is either infected or not, scored as 1 or 0, respectively), we have two distribution families to chose from: binomial or Bernoulli. We will use the **Bernoulli distribution** because it deals with data which only has 1 trial (individual snails) & only 2 possible outcomes (infected or not). On the other hand, if we tested the same individual snails multiple times over a given period, we would be dealing with a binomial distribution.         
* **Link Function**: We will use the less common **complementary log-log (cloglog) link** function (see [here](https://bambinos.github.io/bambi/0.6.0/notebooks/alternative_links_binary.html) for further details). In contrast to the more well-known alternatives (logit and probit), cloglog is much better suited for binary data wherein the one of the outcomes is rare relative to the other, which is the case for us (there are far fewer infected snails than there are uninfected snails; Figure <span style="color: red;">**1.1**</span>)  
* We use a relatively standard number of **MCMC chains** (3), each with 15000 **iterations** and a **burn-in** of 5000. Moreover, we **thin** by 3: a reasonable trade-off between information content and manageable model output file size.   
* Finally, since these models are fitted in STAN (rather than e.g., JAGS or BUGS) with minimally informative priors (see [here](https://www.martinmodrak.cz/2018/02/19/taming-divergences-in-stan-models/) for and excellent crash-course), we avoid divergent transitions by specifying **adapt_delta** to 0.999.   

<br/>
<br/>

## 1st Iteration
<br/>

### Fit model w/ 'survey' as random variable

```{r drop_V2, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
### Generate model output using new formulation
max_V2 <-brm(data = snailDF.na, 
             family = bernoulli(link = cloglog), 
             formula = Sh_all ~ # Response variable
               wbtype2 + wlevel + depth + temp + ph + # Fixed effects
               (1|survey) + (1|shehia/site), # Random effects w/ interaction
             warmup = 5000, # burn-in period (i.e. iterations to be discarded)
             iter = 15000, # total number of iterations (inc. burn-in)
             chains = 3, # number of MCMC chains
             inits  = 0,  # starting values of the iterations
             seed = 666, # random seed, allowing for replication of results
             thin = 3, # thinning for manageable model output file size
             control = list(adapt_delta = 0.999)) 
### Check for convergence and divergent transitions before saving output
max_V2 # No issues
saveRDS(max_V2, "../Data/ModelOutputs/InfectionPrevalence/max_V2.rds")
```
<br/>
<br/>

### Inspect maximal model output

After ensuring that all parameter estimates of the model we just fitted have converged (i.e, Rhat < 1.1; [Gelman & Rubin, 1992](https://www.jstor.org/stable/2246093?seq=1)) and that the 'brms' package doesn't flag any other obvious reasons for concern (e.g., divergent transitions) in the above code chunk, we visually investigate the estimated parameter distributions' chains as well as their posterior distributions (density and trace plots).    
<br/>
<br/>
```{r drop_V2-inspect, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
require("brms"); require("PerformanceAnalytics"); require("ggplot2"); require("ggpubr")
# Read model output
max_V2 <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max_V2.rds")
# Produce density and trace plots
plot(max_V2)
```
<br/>
<br/>

Given the 'complexity' of the model formulation, the density plots (left-hand side) are not hugely informative at this point. However, the trace plots (right-hand side) look nice ('furry caterpillars') for all of the most important parameters except for the 'sd_survey__Intercept' (last panel), where we would like some improvement (but note that it is by no means awful). The model seems to struggle somewhat with fitting the  random variable 'survey', as evident from quite a few divergences withing all chains (including the third and last, which we expect to be the best fitting one). 
<br/>

We know that we must drop one of the two continuous variables dues to their high level of correlation (Figure <span style="color: red;">**1.2**</span>), which we will accomplish through leave-one-out cross-validation (LOOCV). Hopefully, this will improve the 'survey'-variable fit, but first we will refit the maximal model dropping each continuous explanatory variable in turn (below code chunk). Note that we are not dropping any further explanatory variables as these form part of TP's hypotheses-testing. 

<br/>
<br/>

### Fit leave-one-out models

```{r V2-drop1, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
### Fit model dropping temperature
V2_drop_temp <-brm(data = snailDF.na,family = bernoulli(link = cloglog), 
              formula = Sh_all ~ wbtype2 + wlevel + depth + ph +
               (1|survey) + (1|shehia/site), 
             warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666,
             thin = 3, control = list(adapt_delta = 0.999)) 
### Fit model dropping pH
V2_drop_ph <-brm(data = snailDF.na, family = bernoulli(link = cloglog), 
                 formula = Sh_all ~ wbtype2 + wlevel + depth + temp + 
                   (1|survey) + (1|shehia/site),
                 warmup = 5000, iter = 15000, chains = 3, inits  = 0, seed = 666,
                 thin = 3, control = list(adapt_delta = 0.999)) 
### Check for convergence and divergent transitions before saving output
V2_drop_temp#; V2_drop_ph 
saveRDS(V2_drop_temp, "../Data/ModelOutputs/InfectionPrevalence/V2_drop_temp.rds")
#saveRDS(V2_drop_ph, "../Data/ModelOutputs/InfectionPrevalence/V2_drop_ph.rds")
```
<br/>
<br/>


### Model Comparison: Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) 


We use the loo package to carry out Pareto smoothed importance-sampling leave-one-out cross-validation (PSIS-LOO) for purposes of model checking and model comparison.   
- Reference: https://link.springer.com/article/10.1007/s11222-016-9696-4  
- Useful link: https://mc-stan.org/loo/articles/loo2-example.html   



```{r PSISLOO-V2-1st, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
require("brms")
library("loo")
### Read objects
max_V2 <- readRDS("../Data/ModelOutputs/InfectionPrevalence/max_V2.rds")
V2_drop_temp <- readRDS("../Data/ModelOutputs/InfectionPrevalence/V2_drop_temp.rds")
V2_drop_ph <- readRDS("../Data/ModelOutputs/InfectionPrevalence/V2_drop_ph.rds")

### Compare PSIS-LOO values computed with the loo-function 
loo_compare(loo(max_V2, save_psis = TRUE),
            loo(V2_drop_temp, save_psis = TRUE),
            loo(V2_drop_ph, save_psis = TRUE))
```
<br/>
<br/>







<br/>
<br/>
<br/>

# 4. Results

<br/>
<br/>

#### Use this method for visualisation:

* https://stats.stackexchange.com/questions/45444/how-do-you-visualize-binary-outcomes-versus-a-continuous-predictor (Added **December 2020**)  




<br/>
<br/>
<br/>
<br/>
<br/>



# Old scrip below - IGNORE

### Final model

```{r glmer1.17, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
library(arm)

df.na.glmer1.17 <- glmer(Sh_all ~ (1|shehia.x/site.x) +
                           wlevel + temp + ph,
                            data = df.na.rem, 
                         family = binomial(link = "logit"),
                         glmerControl("bobyqa"))


AF1 <- allFit(df.na.glmer1.17, verbose=T)
```




#### Overview

Chapter 7.4 of this https://bookdown.org/schmettow/NewStats/GLM.html was brilliant at explaining hot to interpret these outputs!!!!

```{r (df.na.glmer1.17-Overview, cache=TRUE, eval=FALSE}
require(effects)
plot(allEffects(df.na.glmer1.17))
summary(df.na.glmer1.17)
```
\n
\n




#### Water level
**wlevel**: The effect of water level on whether snails are infected or not is statistically significantly positively linear AND negatively quadratic! (since the wlevel.L and wlevel.Q terms are significant). In other words, going from "1" to "2" to "3", the probability of snails being infected increases BUT due to the negative quadratic term, we know that the rate of increase in probability of infection decreases and becomes a negative trend at a certain point. From above plot, its  obvious that "2" has most infections, i.e. infection rate increases from "1" to "2" and decreases from "2" to "3". We can use the "emmeans" to get the estimated probability of snails being infected in each of the water level types and the function automatically back-transforms estimates for us. For instance, the probability of a snail being infected in water level "1" is 0.00132 (+-0.000732)/0.132% of snails are infected.
```{r df.na.glmer1.17-wlevel, cache=TRUE, eval=FALSE}
require(emmeans)
emmeans(df.na.glmer1.17, c("wlevel"), data = df.na.rem, type = "response")
```


\n
\n


#### Temperature
**temp**: Temperature has a statistically significant positive effect on whether snails are infected, i.e. with increasing temperatures snails are more likely ti be infected. Averaged over the different water levels, as temperature increases by one degree celsius, the odds of snails being infected increase by a factor of 1.249233 (exp(0.22253))/ increase by 24.9233% (+- 6.3564% (exp(0.22253+0.04963)-exp(0.22253)*100)).

E.g. see below that at 27.5 degrees C, the probability of any given snail being infected is 0.00431; therefore, at 28.5 degrees, the odds of a snail being infected is 0.005384194 (0.00431*1.249233)
\n
```{r df.na.glmer1.17-temp, cache=TRUE, eval=FALSE}
require(emmeans)
emmeans(df.na.glmer1.17, c("temp"), data = df.na.rem, type = "response")
exp(0.22253)
```



#### ph
**pH**: ph has a statistically significant negative effect on whether snails are infected, i.e. with increasing ph snails are less likely to be infected. Averaged over the different water levels, as ph increases by one unit, the odds of snails being infected decrease by a factor of 0.4326224 (exp(-0.83789))/ decrease by 56.73776% (1-0.4326224 x 100).

E.g. see below that at ph = 7.01, the probability of asnail being infected is 0.00431; therefore, at ph = 8.01, the odds of a snail being infected is 0.001864603 (0.00431*0.4326224)
\n
```{r df.na.glmer1.17-ph, cache=TRUE, eval=FALSE}
require(emmeans)
emmeans(df.na.glmer1.17, c("ph"), data = df.na.rem, type = "response")
exp(-0.83789)*100
```


\n
\n

### Spatial autocorrelation
\n
\n


```{r spatial-corr-snail-level, cache=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
require(gstat)
require(lme4)
require(sp)

# Snail - gen test
df1 <- read.csv("../Data/TempTom/snail_data_xeno_v1.csv")

# Survey - environmetal variables + human activities
df2 <- read.csv("../Data/TempTom/survey_site_data_xeno_v1.csv")

# Region (Shehia) - schisto prevalence among school childern per region
shehiaRaw <- read.csv("../Data/TempTom/shehia_school_data_v1.csv")

## Set Snail variables as factors
df1$`snail_id`<-as.factor(df1$`snail_id`)
df1$`site`<-as.factor(df1$`site`)
df1$`survey`<-as.factor(df1$`survey`)
df1$`shehia`<-as.factor(df1$`shehia`)
df1$`type`<-as.factor(df1$`type`)
df1$`zest_arm`<-as.factor(df1$`zest_arm`)
df1$`survey_site`<-as.factor(df1$`survey_site`)
df1$`survey_shehia`<-as.factor(df1$`survey_shehia`)
df1$`wbtype`<-as.factor(df1$`wbtype`)
df1$`wbtype2`<-as.factor(df1$`wbtype2`)
df1$`assumed_Bulinus_spp_site`<-as.factor(df1$`assumed_Bulinus_spp_site`)
df1$`ITS-1-2-F_outcome`<-as.factor(df1$`ITS_1_2_F_outcome`)
df1$prepat_schisto_sp<-as.factor(df1$prepat_schisto_sp)
df1$prepat_Sh<-as.factor(df1$prepat_Sh)
df1$prepat_Sb<-as.factor(df1$prepat_Sb)
df1$prepat_ShSb<-as.factor(df1$prepat_ShSb)
df1$prepat_Schisto<-as.factor(df1$prepat_Schisto)
df1$Sh_all<-as.character(df1$Sh_all)
df1$Sh_all<-as.integer(df1$Sh_all)
df1$Sb_all<-as.character(df1$Sb_all)
df1$Sb_all<-as.integer(df1$Sb_all)
df1$'ITSF_2_outcome'<-as.factor(df1$'ITSF_2_outcome')
## have excluded the seq code columns for now could remove ##
df1$'conf_Bulinus_sp'<-as.factor(df1$'conf_Bulinus_sp')
df1$'Bulinus_haplo'<-as.factor(df1$'Bulinus_haplo')
df1$patent_Sh<-as.factor(df1$patent_Sh)
df1$patent_Sb<-as.factor(df1$patent_Sb)
df1$patent_Schisto<-as.factor(df1$patent_Schisto)

# NB can check that variables converted to factor by #
print(is.factor(df1$snail_id))

## Set Site Survey variables as factors
df2$`site`<-as.factor(df2$`USI`)
df2$`survey`<-as.factor(df2$`survey`)
df2$`shehia`<-as.factor(df2$`shehia`)
df2$`type`<-as.factor(df2$`type`)
df2$`zest_arm`<-as.factor(df2$`zest_arm`)
df2$`survey_site`<-as.factor(df2$`survey_site`)
df2$`survey_shehia`<-as.factor(df2$`survey_shehia`)
df2$`wbtype`<-as.factor(df2$`wbtype`)
df2$`wbtype2`<-as.factor(df2$`wbtype2`)
df2$`wlevel`<-as.factor(df2$`wlevel`)
df2$`BgBn_pres`<-as.factor(df2$`BgBn_pres`)
df2$`cerc_sp`<-as.factor(df2$`cerc_sp`)
df2$`flow`<-as.factor(df2$`flow`)
df2$`depth`<-as.factor(df2$`depth`)
df2$`Bfor_pres`<-as.factor(df2$`Bfor_pres`)
df2$`Lym_pres`<-as.factor(df2$`Lym_pres`)
df2$`Mel_pres`<-as.factor(df2$`Mel_pres`)
df2$`Cleo_pres`<-as.factor(df2$`Cleo_pres`)
df2$`Pila_pres`<-as.factor(df2$`Pila_pres`)
df2$`Lan_pres`<-as.factor(df2$`Lan_pres`)
df2$`Thiara_pres`<-as.factor(df2$`Thiara_pres`)
df2$`other_snail`<-as.factor(df2$`other_snail`)
df2$`Lilies`<-as.factor(df2$`Lilies`)
df2$`rushes`<-as.factor(df2$`rushes`)
df2$`rice`<-as.factor(df2$`rice`)
df2$waterhyacinth<-as.factor(df2$waterhyacinth)
df2$palmfronds<-as.factor(df2$palmfronds)
df2$sedge<-as.factor(df2$sedge)
df2$grass<-as.factor(df2$grass)
df2$banana<-as.factor(df2$banana)
df2$veg_any<-as.factor(df2$veg_any)
df2$mud<-as.factor(df2$mud)
df2$sand<-as.factor(df2$sand)
df2$rock<-as.factor(df2$rock)
df2$concrete<-as.factor(df2$concrete)
df2$roots<-as.factor(df2$roots)
df2$Litter<-as.factor(df2$Litter)
df2$`Dead.wood`<-as.factor(df2$`Dead.wood`)
df2$wudu<-as.factor(df2$wudu)
df2$bathing<-as.factor(df2$bathing)
df2$clothes<-as.factor(df2$clothes)
df2$dishes<-as.factor(df2$dishes)
df2$carbike<-as.factor(df2$carbike)
df2$collectingwater<-as.factor(df2$collectingwater)
df2$swimmingplaying<-as.factor(df2$swimmingplaying)
df2$fishing<-as.factor(df2$fishing)
df2$Ricecult<-as.factor(df2$Ricecult)
df2$otherfarming<-as.factor(df2$otherfarming)
df2$sanitation<-as.factor(df2$sanitation)
df2$water_contact<-as.factor(df2$water_contact)
df2$cow<-as.factor(df2$cow)
df2$goat<-as.factor(df2$goat)
df2$donkey<-as.factor(df2$donkey)
df2$ungulate<-as.factor(df2$ungulate)


## Set shehia school as factors
shehiaRaw$`shehia`<-as.factor(shehiaRaw$`shehia`)
shehiaRaw$`type`<-as.factor(shehiaRaw$`type`)
shehiaRaw$`zest_arm`<-as.factor(shehiaRaw$`zest_arm`)


#### Merging datasets for further analysis ####

## merge snail_data with survey_site data ##

# perfrom merge
merge(df1, df2, by.x="survey_site", by.y="survey_site", all.x=TRUE) -> mdf1
# write csv
write.csv(mdf1, "../Data/TempTom/mdf1.csv")

## merge mdf1 data with shehia (schistosomiasis prevalence) data 
# perform merge
merge(mdf1, df3, by.x="shehia.x", by.y="shehia", all.x=TRUE) -> mdf2
write.csv(mdf2, "../Data/TempTom//mdf2.csv")

#### KEEPING COLUMNS of interest FOR FINAL MODEL ####

# created new df with only the columns of interest #

df = mdf2[c("shehia.x", "site.x", "lat_Cor", "lon_Cor", 
            "Sh_all", "wlevel", "temp", "ph")]

# also created a na.omit df, however can specifiy this in the models
df.na <- na.omit(df)

# also created a data set removing the 'low values' sites Mat12 Mat7 Wam7 Ole13 Waw5 Uku10 
library(Hmisc)
library(dplyr)
df.na.rem1 <- filter(df.na, site.x != "Mat7")
df.na.rem2 <- filter(df.na.rem1, site.x != "Mat12")
df.na.rem3 <- filter(df.na.rem2, site.x != "Wam7")
df.na.rem4 <- filter(df.na.rem3, site.x != "Ole13")
df.na.rem5 <- filter(df.na.rem4, site.x != "Waw5")
df.na.rem <- filter(df.na.rem5, site.x != "Uku10")
library(effects)

# creating ordered variables for wlevel (as for other models)
df.na.rem$wlevel <- factor(df.na.rem$wlevel, ordered = TRUE, 
                                levels = c("1", "2", "3", "4"))

# run final model 
library(arm)
library(lme4)
df.na.glmer1.17 <- glmer(Sh_all ~ (1|shehia.x/site.x) +
                           wlevel + temp + ph,
                            data = df.na.rem, 
                         family = binomial(link = "logit"),
                         glmerControl("bobyqa"))

df.na.glmer1.17 <- glmer(Sh_all ~ (1|shehia.x/site.x) +
                           wlevel + temp + ph,
                            data = df.na.rem, 
                         family = binomial(link = "logit"),
                         glmerControl("bobyqa"))


# Find residuals from response variable of final model
E <- residuals(df.na.glmer1.17, type = "response")
#E <- resid(df.na.glmer1.17)

snailDF_res <- data.frame(E, df.na.rem$lat_Cor, df.na.rem$lon_Cor)

coordinates(snailDF_res) <- c("df.na.rem.lat_Cor", "df.na.rem.lon_Cor")

bubble(snailDF_res, "E", col = c("black", "grey"),
       main = "Residuals", xlab = "X-coordinates",
       ylab = "Y-coordinates")

Vario1 <- variogram(E ~ 1, snailDF_res)
plot(Vario1)
```




###!!!! USE Residuals() from BinomTools package (not available for my curr. R version )




