---
title: "02-SnailLevel"
author: "Galina M. Jönsson"
date: "16/10/2020"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

## The data

Load and tidy the data. These analyses are based on the data sets, each of which contains data on different levels: snail-level, survey-level and Shehia-level. We therefore start by loading each one in turn and assigning all variables within a data set the correct class.

### Raw data
```{r load-data, cache=TRUE, warning=FALSE, message=FALSE}
#############################################################################
####### Snail-level data set - test result for infection per snail ##########
#############################################################################

# Load data set
snailRaw <- read.csv("../Data/snail_data_xeno_v1.csv")

## Assign variables appropriate classes
snailRaw$`snail_id`<-as.factor(snailRaw$`snail_id`)
snailRaw$`site`<-as.factor(snailRaw$`site`)
snailRaw$`survey`<-as.factor(snailRaw$`survey`)
snailRaw$`shehia`<-as.factor(snailRaw$`shehia`)
snailRaw$`type`<-as.factor(snailRaw$`type`)
snailRaw$`zest_arm`<-as.factor(snailRaw$`zest_arm`)
snailRaw$`survey_site`<-as.factor(snailRaw$`survey_site`)
snailRaw$`survey_shehia`<-as.factor(snailRaw$`survey_shehia`)
snailRaw$`wbtype`<-as.factor(snailRaw$`wbtype`)
snailRaw$`wbtype2`<-as.factor(snailRaw$`wbtype2`)
snailRaw$`assumed_Bulinus_spp_site`<-as.factor(snailRaw$`assumed_Bulinus_spp_site`)
snailRaw$`ITS-1-2-F_outcome`<-as.factor(snailRaw$`ITS_1_2_F_outcome`)
snailRaw$prepat_schisto_sp<-as.factor(snailRaw$prepat_schisto_sp)
snailRaw$prepat_Sh<-as.factor(snailRaw$prepat_Sh)
snailRaw$prepat_Sb<-as.factor(snailRaw$prepat_Sb)
snailRaw$prepat_ShSb<-as.factor(snailRaw$prepat_ShSb)
snailRaw$prepat_Schisto<-as.factor(snailRaw$prepat_Schisto)
snailRaw$Sh_all<-as.character(snailRaw$Sh_all)
snailRaw$Sh_all<-as.integer(snailRaw$Sh_all)
snailRaw$Sb_all<-as.character(snailRaw$Sb_all)
snailRaw$Sb_all<-as.integer(snailRaw$Sb_all)
snailRaw$'ITSF_2_outcome'<-as.factor(snailRaw$'ITSF_2_outcome')
snailRaw$'conf_Bulinus_sp'<-as.factor(snailRaw$'conf_Bulinus_sp')
snailRaw$'Bulinus_haplo'<-as.factor(snailRaw$'Bulinus_haplo')
snailRaw$patent_Sh<-as.factor(snailRaw$patent_Sh)
snailRaw$patent_Sb<-as.factor(snailRaw$patent_Sb)
snailRaw$patent_Schisto<-as.factor(snailRaw$patent_Schisto)






#############################################################################
#### Survey-level data set - environmental variables + human activities #####
#############################################################################

# Load data set
surveyRaw <- read.csv("../Data/survey_site_data_xeno_v1.csv")

## Assign variables appropriate classes
surveyRaw$`site`<-as.factor(surveyRaw$`USI`)
surveyRaw$`survey`<-as.factor(surveyRaw$`survey`)
surveyRaw$`shehia`<-as.factor(surveyRaw$`shehia`)
surveyRaw$`type`<-as.factor(surveyRaw$`type`)
surveyRaw$`zest_arm`<-as.factor(surveyRaw$`zest_arm`)
surveyRaw$`survey_site`<-as.factor(surveyRaw$`survey_site`)
surveyRaw$`survey_shehia`<-as.factor(surveyRaw$`survey_shehia`)
surveyRaw$`wbtype`<-as.factor(surveyRaw$`wbtype`)
surveyRaw$`wbtype2`<-as.factor(surveyRaw$`wbtype2`)
surveyRaw$`wlevel`<-as.factor(surveyRaw$`wlevel`)
surveyRaw$`BgBn_pres`<-as.factor(surveyRaw$`BgBn_pres`)
surveyRaw$`cerc_sp`<-as.factor(surveyRaw$`cerc_sp`)
surveyRaw$`flow`<-as.factor(surveyRaw$`flow`)
surveyRaw$`depth`<-as.factor(surveyRaw$`depth`)
surveyRaw$`Bfor_pres`<-as.factor(surveyRaw$`Bfor_pres`)
surveyRaw$`Lym_pres`<-as.factor(surveyRaw$`Lym_pres`)
surveyRaw$`Mel_pres`<-as.factor(surveyRaw$`Mel_pres`)
surveyRaw$`Cleo_pres`<-as.factor(surveyRaw$`Cleo_pres`)
surveyRaw$`Pila_pres`<-as.factor(surveyRaw$`Pila_pres`)
surveyRaw$`Lan_pres`<-as.factor(surveyRaw$`Lan_pres`)
surveyRaw$`Thiara_pres`<-as.factor(surveyRaw$`Thiara_pres`)
surveyRaw$`other_snail`<-as.factor(surveyRaw$`other_snail`)
surveyRaw$`Lilies`<-as.factor(surveyRaw$`Lilies`)
surveyRaw$`rushes`<-as.factor(surveyRaw$`rushes`)
surveyRaw$`rice`<-as.factor(surveyRaw$`rice`)
surveyRaw$waterhyacinth<-as.factor(surveyRaw$waterhyacinth)
surveyRaw$palmfronds<-as.factor(surveyRaw$palmfronds)
surveyRaw$sedge<-as.factor(surveyRaw$sedge)
surveyRaw$grass<-as.factor(surveyRaw$grass)
surveyRaw$banana<-as.factor(surveyRaw$banana)
surveyRaw$veg_any<-as.factor(surveyRaw$veg_any)
surveyRaw$mud<-as.factor(surveyRaw$mud)
surveyRaw$sand<-as.factor(surveyRaw$sand)
surveyRaw$rock<-as.factor(surveyRaw$rock)
surveyRaw$concrete<-as.factor(surveyRaw$concrete)
surveyRaw$roots<-as.factor(surveyRaw$roots)
surveyRaw$Litter<-as.factor(surveyRaw$Litter)
surveyRaw$`Dead.wood`<-as.factor(surveyRaw$`Dead.wood`)
surveyRaw$wudu<-as.factor(surveyRaw$wudu)
surveyRaw$bathing<-as.factor(surveyRaw$bathing)
surveyRaw$clothes<-as.factor(surveyRaw$clothes)
surveyRaw$dishes<-as.factor(surveyRaw$dishes)
surveyRaw$carbike<-as.factor(surveyRaw$carbike)
surveyRaw$collectingwater<-as.factor(surveyRaw$collectingwater)
surveyRaw$swimmingplaying<-as.factor(surveyRaw$swimmingplaying)
surveyRaw$fishing<-as.factor(surveyRaw$fishing)
surveyRaw$Ricecult<-as.factor(surveyRaw$Ricecult)
surveyRaw$otherfarming<-as.factor(surveyRaw$otherfarming)
surveyRaw$sanitation<-as.factor(surveyRaw$sanitation)
surveyRaw$water_contact<-as.factor(surveyRaw$water_contact)
surveyRaw$cow<-as.factor(surveyRaw$cow)
surveyRaw$goat<-as.factor(surveyRaw$goat)
surveyRaw$donkey<-as.factor(surveyRaw$donkey)
surveyRaw$ungulate<-as.factor(surveyRaw$ungulate)




#############################################################################
###### Shehia-level data set - infection rates among school children ########
#############################################################################

# Load data set
shehiaRaw <- read.csv("../Data/shehia_school_data_v1.csv")

## Assign variables appropriate classes
shehiaRaw$`shehia`<-as.factor(shehiaRaw$`shehia`)
shehiaRaw$`type`<-as.factor(shehiaRaw$`type`)
shehiaRaw$`zest_arm`<-as.factor(shehiaRaw$`zest_arm`)

```


### Tidy raw data
Now we merge the data sets to get one data set where each individual *Bulinus* individual (snailRaw) also has information on environmental variables from where it was collected (surveyRaw) and infection rates among school children in the Shehia from where it was collected (shehiaRaw). Finally, we tidy the resulting data set. 
```{r MergeTidy-data, cache=TRUE, warning=FALSE, message=FALSE}


### Merge snailRaw and surveyRaw based on "survey_site" and keep all observations in snailRaw
snailDFtemp1 <- merge(snailRaw, surveyRaw, by.x="survey_site", by.y="survey_site", all.x=TRUE)

# write.csv(snailDFtemp1, "../Data/mdf1.csv")

# Double check we haven't lost/duplicated any observations
nrow(snailRaw) == nrow(snailDFtemp1) 



### Merge snailDFtemp1 and shehiaRaw based on shehia and keep all observations in snailRaw/snailDFtemp1
snailDFtemp2 <-merge(snailDFtemp1, shehiaRaw, by.x="shehia.x", by.y="shehia", all.x=TRUE)

#write.csv(snailDFtemp2, "../Data/mdf2.csv")

# Double check we haven't lost/duplicated any observations
nrow(snailRaw) == nrow(snailDFtemp2) 





### Subset columns of interest and create a new data frame with only these columns
snailDF <- snailDFtemp2[c("shehia.x", "survey_site", "snail_id", 
                        "site.x", "survey.x", "type.x",
                        "zest_arm.x", "survey_shehia.x", "wbtype.x", 
                        "wbtype2.x", "lat_Cor", "lon_Cor",
                        "assumed_Bulinus_spp_site", "Sh_all", "Sb_all", 
                        "wlevel", "BgBn_number", "temp", 
                        "ph", "cond", "tds", 
                        "do", "sal", "flow", 
                        "depth", "Bfor_pres", "Lym_pres", 
                        "Mel_pres", "Cleo_pres", "Pila_pres", 
                        "Lan_pres", "Thiara_pres", "other_snail", 
                        "Lilies", "rushes", "rice", 
                        "waterhyacinth", "palmfronds", "sedge", 
                        "grass", "banana", "veg_any", 
                        "mud", "sand", "rock", 
                        "concrete", "roots", "Litter", 
                        "Dead.wood", "wudu", "bathing", 
                        "clothes", "dishes", "carbike", 
                        "collectingwater", "swimmingplaying", 
                        "fishing", "Ricecult", "otherfarming", 
                        "sanitation", "water_contact", "cow", 
                        "goat", "donkey", "ungulate",
                        "prev_2012", "prev_2013", "prev_2014", 
                        "prev_2015", "prev_2016", "eggs_2012", 
                        "eggs_2013", "eggs_2014", "eggs_2015", 
                        "eggs_2016", "prev_change_12_16", "eggs_change_12_16",
                        "survey_date")]




### Rename certain variables for convenience
require(dplyr)
snailDF <- snailDF %>% 
  rename(
    shehia = shehia.x, 
    site = site.x, 
    survey = survey.x, 
    type = type.x, 
    zest_arm = zest_arm.x, 
    survey_shehia = survey_shehia.x, 
    wbtype = wbtype.x,
    wbtype2 = wbtype2.x
    )


# As we will use "site" nested in "shehia" as random variables, we will remove any sites with six or fewer snails. See the number of snails in each site commented next to the site name below
#library(Hmisc)
temp <- nrow(snailDF)
snailDF <- filter(snailDF, site != "Mat7") # 3
snailDF <- filter(snailDF, site != "Mat12") # 3
snailDF <- filter(snailDF, site != "Wam7") # 3
snailDF <- filter(snailDF, site != "Ole13") # 6
snailDF <- filter(snailDF, site != "Waw5") # 5
snailDF <- filter(snailDF, site != "Uku10") # 6

# How many observations were removed?
temp - nrow(snailDF)


### Create ordered variables for type and wlevel
snailDF$type <- factor(snailDF$type, ordered = TRUE, 
                                levels = c("HNR", "HD", "LNR", "LD"))
snailDF$wlevel <- factor(snailDF$wlevel, ordered = TRUE, 
                                levels = c("1", "2", "3", "4"))




### Also create a data frame where all observations have data for all above variables
snailDF.na <- na.omit(snailDF)

# How many observations were removed?
nrow(snailDF) - nrow(snailDF.na)

# Drop levels from both tidied data sets
snailDF <- droplevels(snailDF)
snailDF.na <- droplevels(snailDF.na)
```



### Inspect response variable
The response variable used in these analyses is "Sh_all", which denotes whether **TOM** fill in please. 

As we will be preforming our model selection using the snailDF.na data set, we inspect its variables. 
```{r respvar, cache=TRUE, message=FALSE}
require(ggplot2)
require(dplyr)

### How many **TOM** fill in please are **infected**? 
snailDF.na %>% 
  mutate(y = Sh_all %>% as.character()) %>% 
  ggplot(aes(x = Sh_all)) +
  geom_bar() +
  theme(panel.grid = element_blank())


table(snailDF.na$Sh_all)
```

97%, i.e. the majority, of tested individuals were not infected (5101), whilst 3% were (158). 


### Test for collinearity between explanatory variables
\n
\n
#### Explanatory variables of potential interest
* **wlevel** -> water level    
* **wbtype2** -> waterbody type: either permanent or temporary    
* **syrvey** -> four surveys; corresponds to time of year; potentially correlated with wlevel and wbtype2    
* **temp** -> water temperature   
* **cond** -> conductivity; indirect measure of water chemistry   
* **ph** -> potentially correlated with conductivity   
* **type** -> human response to treatment; whether people got reinfected quickly or not; four categories    


Potential collinearity between quantitative explanatory variables is tested using the Kendall rank coefficient to establish whether variables are statistically dependent. This test is non-parametric, i.e. does not rely on any assumptions on the distributions of the variables. Collinearity between qualitative and quantitative explanatory variables is visually examined using box plots. 
```{r collinearity-explanVars-test, message=FALSE, warning=FALSE, cache=TRUE}
require("PerformanceAnalytics")
require("ggplot2")
require("ggpubr")



### Quantitative explanatory variables: Kendall rank coefficient
chart.Correlation(snailDF.na[,c("temp", "ph", "cond")], 
                  histogram=TRUE, pch=19, method = "kendall")



### Qualitative and quantitative explanatory variables

## Qualitative variables and temp
ggarrange(ggplot(snailDF.na, aes(x = type, y = temp)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = wbtype2, y = temp)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = survey, y = temp)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = wlevel, y = temp)) + geom_boxplot() + rremove("x.text"), 
          labels = c("type", "wbtype2", "survey", "wlevel"),
          ncol = 2, nrow = 2)

## Qualitative variables and pH
ggarrange(ggplot(snailDF.na, aes(x = type, y = ph)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = wbtype2, y = ph)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = survey, y = ph)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = wlevel, y = ph)) + geom_boxplot() + rremove("x.text"), 
          labels = c("type", "wbtype2", "survey", "wlevel"),
          ncol = 2, nrow = 2)

## Qualitative variables and pH
ggarrange(ggplot(snailDF.na, aes(x = type, y = cond)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = wbtype2, y = cond)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = survey, y = cond)) + geom_boxplot(),
          ggplot(snailDF.na, aes(x = wlevel, y = cond)) + geom_boxplot() + rremove("x.text"), 
          labels = c("type", "wbtype2", "survey", "wlevel"),
          ncol = 2, nrow = 2)
```


\n

All three explanatory quantitative variables (temperature, conductivity and pH) are correlated (p<0.001), and therefore not independent. Temperature and pH are negatively correlated (p<0.001), whilst conductivity is positively correlated with both temperature and pH. As such, by the end of the model selection process we want a model that **ONLY includes one quantitative variable**, as including two or more independent variables does not meet model assumptions. 


Neither of the qualitative explanatory variables are clearly correlated with any of the quantitative explanatory variables. 

## Model fitting and selection

The variables used in initial model selection are as follows: 

#### Response variable 
* **Sh_all** -> **TOM** fill in please. 


#### Explanatory variables of potential interest
* **wlevel** -> water level    
* **wbtype2** -> waterbody type: either permanent or temporary    
* **syrvey** -> four surveys; corresponds to time of year; potentially correlated with wlevel and wbtype2; this vaiable will not be dropped in any model simplification as it accounts for **known differences in snail abundance** (TOM!?) between different seasons.  
* **temp** -> water temperature   
* **cond** -> conductivity; indirect measure of water chemistry   
* **ph** ->  
* **type** -> human response to treatment; whether people got reinfected quickly or not; four categories    



#### Random factors   
* **shehia** -> regions/wards on Pemba
* **site** -> sites within shesias; hence, site is nested within shehia in models


Given the variables described above, we must use a type of generalised linear mixed effects model to test what effects **Sh_all** **TOM** fill in please. . 





### Distribution
As our data is binary (1 is an individual snail is infected and 0 if not), the choice of distribution (family) is straight forward: we will use a binomial distribution. The link function we will use will depend on the flexibility of model implementation (see below). We will initially try the logit link function; however, given that the logit link function may be inappropriate when the numbers of zeroes and ones are very unequal (as our data is), if possible, we will also try the clog-log and clog-clog links. 


### Model implementation selection
Given the inherently "low information content" of binary data, we will fit our binomial generalised linear mixed effects model using Bayesian inferences. We will use the R package "brms", which implements Bayesian generalized linear mixed models using the probabilistic programming language Stan. Please see the [brms github page](https://github.com/paul-buerkner/brms) for software installation guides (available for multiple operation systems). Moreover, "brms" allows model fit to be assessed and compared with the Watanabe-Akaike-Information Criterion (WAIC) and leave-one-out cross-validation (LOO).


### Prior specifications
We apply prior distributions to all explanatory variables of potential interest that reflect our actual beliefs and understandings. Our explanatory variables and prior specifications are as follows:
* **wlevel** -> water level    
* **wbtype2** -> waterbody type: either permanent or temporary    
* **syrvey** -> four surveys; corresponds to time of year; potentially correlated with wlevel and wbtype2; this variable will not be dropped in any model simplification as it accounts for **known differences in ??????** (TOM!?) between different seasons.  
* **temp** -> water temperature in degrees Celsius per survey within the range 22.33C to 33.81C. Although multiple authors (**TOM** examples) have shown that **TOM** the snail/the parasite is limited by temperature (BREIF EXPLINATION), we know/do not know whether it is within the temperature ranges tested here. As such we chose a prior distribution that reflects our this knowledge/lack thereof: a normal prior with mean 0/1/2/3/4**????** and standard deviation 10    
* **cond** -> conductivity, which is an indirect measure of water chemistry   
* **ph** ->  
* **type** -> human response to treatment (i.e. the degree to which infected individuals became reinfected) per shehia, which is divided into four categories. We expect responses to treatment to be an indirect measure of human behavior (**TOM!!??**), such that individuals inhabiting shesias with low rates of reinfection are more likely to exhibit less "risky" behaviors compared to those inhabiting Shesias with high rates of reinfection. Hence, we use a       

(set_prior("normal(0,10)", class = "b"

"Families binomial, bernoulli, Beta, zero_inflated_binomial, zero_inflated_beta, and zero_one_inflated_beta support logit, probit, probit_approx, cloglog, cauchit, and identity."


##### Useful links
* https://mran.microsoft.com/snapshot/2016-02-05/web/packages/brms/vignettes/brms.pdf   
* https://bookdown.org/ajkurz/DBDA_recoded/jags-brms.html    
* https://www.rensvandeschoot.com/tutorials/brms-started/   
* https://www.rensvandeschoot.com/tutorials/brms-priors/   
* https://www.rensvandeschoot.com/brms-wambs/   



```{r Sh_all-priors, message=FALSE, warning=FALSE, cache=TRUE}
require("brms")

### Which priors can we set?
get_prior(Sh_all ~ wbtype2 + wlevel + type + survey +
            temp + cond + ph +
            (1|shehia/site), 
          data = snailDF.na)

### Fit a maximal model with uninformative priors 
max.lowInfo <-
  brm(data = snailDF.na, 
      family = bernoulli(link = logit),
      formula = Sh_all ~ wbtype2 + wlevel + type + survey +
            temp + cond + ph +
            (1|shehia/site), 
      prior = c(set_prior("normal(0,100)", class = "b"),
                set_prior("cauchy(0,20)", class = "sd")),
      warmup = 5000, iter = 15000, chains = 3,
      inits  = "random")


summary(max.lowInfo)

plot(max.lowInfo)
```


# OLD SCRIPT BELOW - IGNORE

## Final model

```{r glmer1.17, message=FALSE, warning=FALSE, cache=TRUE, eval=FALSE}
library(arm)

df.na.glmer1.17 <- glmer(Sh_all ~ (1|shehia.x/site.x) +
                           wlevel + temp + ph,
                            data = df.na.rem, 
                         family = binomial(link = "logit"),
                         glmerControl("bobyqa"))


AF1 <- allFit(df.na.glmer1.17, verbose=T)
```




#### Overview

Chapter 7.4 of this https://bookdown.org/schmettow/NewStats/GLM.html was brilliant at explaining hot to interpret these outputs!!!!

```{r (df.na.glmer1.17-Overview, cache=TRUE, eval=FALSE}
require(effects)
plot(allEffects(df.na.glmer1.17))
summary(df.na.glmer1.17)
```
\n
\n




#### Water level
**wlevel**: The effect of water level on whether snails are infected or not is statistically significantly positively linear AND negatively quadratic! (since the wlevel.L and wlevel.Q terms are significant). In other words, going from "1" to "2" to "3", the probability of snails being infected increases BUT due to the negative quadratic term, we know that the rate of increase in probability of infection decreases and becomes a negative trend at a certain point. From above plot, its  obvious that "2" has most infections, i.e. infection rate increases from "1" to "2" and decreases from "2" to "3". We can use the "emmeans" to get the estimated probability of snails being infected in each of the water level types and the function automatically back-transforms estimates for us. For instance, the probability of a snail being infected in water level "1" is 0.00132 (+-0.000732)/0.132% of snails are infected.
```{r df.na.glmer1.17-wlevel, cache=TRUE, eval=FALSE}
require(emmeans)
emmeans(df.na.glmer1.17, c("wlevel"), data = df.na.rem, type = "response")
```


\n
\n


#### Temperature
**temp**: Temperature has a statistically significant positive effect on whether snails are infected, i.e. with increasing temperatures snails are more likely ti be infected. Averaged over the different water levels, as temperature increases by one degree celsius, the odds of snails being infected increase by a factor of 1.249233 (exp(0.22253))/ increase by 24.9233% (+- 6.3564% (exp(0.22253+0.04963)-exp(0.22253)*100)).

E.g. see below that at 27.5 degrees C, the probability of any given snail being infected is 0.00431; therefore, at 28.5 degrees, the odds of a snail being infected is 0.005384194 (0.00431*1.249233)
\n
```{r df.na.glmer1.17-temp, cache=TRUE, eval=FALSE}
require(emmeans)
emmeans(df.na.glmer1.17, c("temp"), data = df.na.rem, type = "response")
exp(0.22253)
```



#### ph
**pH**: ph has a statistically significant negative effect on whether snails are infected, i.e. with increasing ph snails are less likely to be infected. Averaged over the different water levels, as ph increases by one unit, the odds of snails being infected decrease by a factor of 0.4326224 (exp(-0.83789))/ decrease by 56.73776% (1-0.4326224 x 100).

E.g. see below that at ph = 7.01, the probability of asnail being infected is 0.00431; therefore, at ph = 8.01, the odds of a snail being infected is 0.001864603 (0.00431*0.4326224)
\n
```{r df.na.glmer1.17-ph, cache=TRUE, eval=FALSE}
require(emmeans)
emmeans(df.na.glmer1.17, c("ph"), data = df.na.rem, type = "response")
exp(-0.83789)*100
```


\n
\n

## Spatial autocorrelation
\n
\n


```{r spatial-corr-snail-level, cache=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
require(gstat)
require(lme4)
require(sp)

# Snail - gen test
df1 <- read.csv("../Data/TempTom/snail_data_xeno_v1.csv")

# Survey - environmetal variables + human activities
df2 <- read.csv("../Data/TempTom/survey_site_data_xeno_v1.csv")

# Region (Shehia) - schisto prevalence among school childern per region
shehiaRaw <- read.csv("../Data/TempTom/shehia_school_data_v1.csv")

## Set Snail variables as factors
df1$`snail_id`<-as.factor(df1$`snail_id`)
df1$`site`<-as.factor(df1$`site`)
df1$`survey`<-as.factor(df1$`survey`)
df1$`shehia`<-as.factor(df1$`shehia`)
df1$`type`<-as.factor(df1$`type`)
df1$`zest_arm`<-as.factor(df1$`zest_arm`)
df1$`survey_site`<-as.factor(df1$`survey_site`)
df1$`survey_shehia`<-as.factor(df1$`survey_shehia`)
df1$`wbtype`<-as.factor(df1$`wbtype`)
df1$`wbtype2`<-as.factor(df1$`wbtype2`)
df1$`assumed_Bulinus_spp_site`<-as.factor(df1$`assumed_Bulinus_spp_site`)
df1$`ITS-1-2-F_outcome`<-as.factor(df1$`ITS_1_2_F_outcome`)
df1$prepat_schisto_sp<-as.factor(df1$prepat_schisto_sp)
df1$prepat_Sh<-as.factor(df1$prepat_Sh)
df1$prepat_Sb<-as.factor(df1$prepat_Sb)
df1$prepat_ShSb<-as.factor(df1$prepat_ShSb)
df1$prepat_Schisto<-as.factor(df1$prepat_Schisto)
df1$Sh_all<-as.character(df1$Sh_all)
df1$Sh_all<-as.integer(df1$Sh_all)
df1$Sb_all<-as.character(df1$Sb_all)
df1$Sb_all<-as.integer(df1$Sb_all)
df1$'ITSF_2_outcome'<-as.factor(df1$'ITSF_2_outcome')
## have excluded the seq code columns for now could remove ##
df1$'conf_Bulinus_sp'<-as.factor(df1$'conf_Bulinus_sp')
df1$'Bulinus_haplo'<-as.factor(df1$'Bulinus_haplo')
df1$patent_Sh<-as.factor(df1$patent_Sh)
df1$patent_Sb<-as.factor(df1$patent_Sb)
df1$patent_Schisto<-as.factor(df1$patent_Schisto)

# NB can check that variables converted to factor by #
print(is.factor(df1$snail_id))

## Set Site Survey variables as factors
df2$`site`<-as.factor(df2$`USI`)
df2$`survey`<-as.factor(df2$`survey`)
df2$`shehia`<-as.factor(df2$`shehia`)
df2$`type`<-as.factor(df2$`type`)
df2$`zest_arm`<-as.factor(df2$`zest_arm`)
df2$`survey_site`<-as.factor(df2$`survey_site`)
df2$`survey_shehia`<-as.factor(df2$`survey_shehia`)
df2$`wbtype`<-as.factor(df2$`wbtype`)
df2$`wbtype2`<-as.factor(df2$`wbtype2`)
df2$`wlevel`<-as.factor(df2$`wlevel`)
df2$`BgBn_pres`<-as.factor(df2$`BgBn_pres`)
df2$`cerc_sp`<-as.factor(df2$`cerc_sp`)
df2$`flow`<-as.factor(df2$`flow`)
df2$`depth`<-as.factor(df2$`depth`)
df2$`Bfor_pres`<-as.factor(df2$`Bfor_pres`)
df2$`Lym_pres`<-as.factor(df2$`Lym_pres`)
df2$`Mel_pres`<-as.factor(df2$`Mel_pres`)
df2$`Cleo_pres`<-as.factor(df2$`Cleo_pres`)
df2$`Pila_pres`<-as.factor(df2$`Pila_pres`)
df2$`Lan_pres`<-as.factor(df2$`Lan_pres`)
df2$`Thiara_pres`<-as.factor(df2$`Thiara_pres`)
df2$`other_snail`<-as.factor(df2$`other_snail`)
df2$`Lilies`<-as.factor(df2$`Lilies`)
df2$`rushes`<-as.factor(df2$`rushes`)
df2$`rice`<-as.factor(df2$`rice`)
df2$waterhyacinth<-as.factor(df2$waterhyacinth)
df2$palmfronds<-as.factor(df2$palmfronds)
df2$sedge<-as.factor(df2$sedge)
df2$grass<-as.factor(df2$grass)
df2$banana<-as.factor(df2$banana)
df2$veg_any<-as.factor(df2$veg_any)
df2$mud<-as.factor(df2$mud)
df2$sand<-as.factor(df2$sand)
df2$rock<-as.factor(df2$rock)
df2$concrete<-as.factor(df2$concrete)
df2$roots<-as.factor(df2$roots)
df2$Litter<-as.factor(df2$Litter)
df2$`Dead.wood`<-as.factor(df2$`Dead.wood`)
df2$wudu<-as.factor(df2$wudu)
df2$bathing<-as.factor(df2$bathing)
df2$clothes<-as.factor(df2$clothes)
df2$dishes<-as.factor(df2$dishes)
df2$carbike<-as.factor(df2$carbike)
df2$collectingwater<-as.factor(df2$collectingwater)
df2$swimmingplaying<-as.factor(df2$swimmingplaying)
df2$fishing<-as.factor(df2$fishing)
df2$Ricecult<-as.factor(df2$Ricecult)
df2$otherfarming<-as.factor(df2$otherfarming)
df2$sanitation<-as.factor(df2$sanitation)
df2$water_contact<-as.factor(df2$water_contact)
df2$cow<-as.factor(df2$cow)
df2$goat<-as.factor(df2$goat)
df2$donkey<-as.factor(df2$donkey)
df2$ungulate<-as.factor(df2$ungulate)


## Set shehia school as factors
shehiaRaw$`shehia`<-as.factor(shehiaRaw$`shehia`)
shehiaRaw$`type`<-as.factor(shehiaRaw$`type`)
shehiaRaw$`zest_arm`<-as.factor(shehiaRaw$`zest_arm`)


#### Merging datasets for further analysis ####

## merge snail_data with survey_site data ##

# perfrom merge
merge(df1, df2, by.x="survey_site", by.y="survey_site", all.x=TRUE) -> mdf1
# write csv
write.csv(mdf1, "../Data/TempTom/mdf1.csv")

## merge mdf1 data with shehia (schistosomiasis prevalence) data 
# perform merge
merge(mdf1, df3, by.x="shehia.x", by.y="shehia", all.x=TRUE) -> mdf2
write.csv(mdf2, "../Data/TempTom//mdf2.csv")

#### KEEPING COLUMNS of interest FOR FINAL MODEL ####

# created new df with only the columns of interest #

df = mdf2[c("shehia.x", "site.x", "lat_Cor", "lon_Cor", 
            "Sh_all", "wlevel", "temp", "ph")]

# also created a na.omit df, however can specifiy this in the models
df.na <- na.omit(df)

# also created a data set removing the 'low values' sites Mat12 Mat7 Wam7 Ole13 Waw5 Uku10 
library(Hmisc)
library(dplyr)
df.na.rem1 <- filter(df.na, site.x != "Mat7")
df.na.rem2 <- filter(df.na.rem1, site.x != "Mat12")
df.na.rem3 <- filter(df.na.rem2, site.x != "Wam7")
df.na.rem4 <- filter(df.na.rem3, site.x != "Ole13")
df.na.rem5 <- filter(df.na.rem4, site.x != "Waw5")
df.na.rem <- filter(df.na.rem5, site.x != "Uku10")
library(effects)

# creating ordered variables for wlevel (as for other models)
df.na.rem$wlevel <- factor(df.na.rem$wlevel, ordered = TRUE, 
                                levels = c("1", "2", "3", "4"))

# run final model 
library(arm)
library(lme4)
df.na.glmer1.17 <- glmer(Sh_all ~ (1|shehia.x/site.x) +
                           wlevel + temp + ph,
                            data = df.na.rem, 
                         family = binomial(link = "logit"),
                         glmerControl("bobyqa"))

df.na.glmer1.17 <- glmer(Sh_all ~ (1|shehia.x/site.x) +
                           wlevel + temp + ph,
                            data = df.na.rem, 
                         family = binomial(link = "logit"),
                         glmerControl("bobyqa"))


# Find residuals from response variable of final model
E <- residuals(df.na.glmer1.17, type = "response")
#E <- resid(df.na.glmer1.17)

snailDF_res <- data.frame(E, df.na.rem$lat_Cor, df.na.rem$lon_Cor)

coordinates(snailDF_res) <- c("df.na.rem.lat_Cor", "df.na.rem.lon_Cor")

bubble(snailDF_res, "E", col = c("black", "grey"),
       main = "Residuals", xlab = "X-coordinates",
       ylab = "Y-coordinates")

Vario1 <- variogram(E ~ 1, snailDF_res)
plot(Vario1)
```




###!!!! USE Residuals() from BinomTools package (not available for my curr. R version )




